### 2014-11-14 WaingartenThoughts.tex
initial commit with some thoughts

\title{Erik's thoughts}
\author{
        Erik Waingarten
}
\date{\today}

\documentclass[12pt]{article}
\usepackage{amsmath}

\begin{document}
\maketitle

\section{Question 1}

I argue that there are no rational functions with period 2. This is a simple argument.

Suppose there was a function $f$ of one variable such that $F(x,y) = \dfrac{f(y)}{x}$ had periodicity 2, then $a_0 = a_2 = x$, $a_1 = y$ and
\[ a_2 = x = \dfrac{f(x)}{y} \]
And so $f(x) = xy$, for every $y$, so $f$ is not a function of one variable.

\section{Some periodic functions}

If you have $F(x,y) = \dfrac{1}{x}$, then this is periodic with period $4$. In particular, the sequence looks like:
\[ x, y, \dfrac{1}{x}, \dfrac{1}{y}, x, y, ... \]
An obvious observation is that if $F(x,y) = f(x)$, then $F(x,y)$ is the interlacing of two sequences where sequences start with $x$ and $y$ and one sequence is $a_i = f^{i}(x)$ and $b_i = f^{i}(y)$, and the sequence is $x,y,a_1, b_1, a_2, b_2, ...$.

So if $x = f^{l}(x)$, then the sequence is periodic with period $n = 2l$. If $F(x,y) = f(y)$, then the sequence is not periodic. This is because if $x = a_0 = a_n$ and $a_1 = a_{n+1} = y$, then $f(x) = y$, but this should be true of all $x$, and so $f$ is a constant function. But then it needs to be true for all $y$, which is a contradiction.

Examples of functions and their periods:
\begin{itemize}
\item $F(x, y) = \dfrac{1}{x}$ with period $4$ as shown above.
\item $F(x,y) = \dfrac{c}{x}$ with period $4$. Very similar.
\item $F(x,y) = \dfrac{1}{xy}$ with period $3$.
\item $F(x,y) = \dfrac{y}{x}$ with period $6$.
\item $F(x,y) = x$, with period $2$. 
\end{itemize}

\section{Question 2}

I'm not sure, but I think its the constant polynomials. Suppose we had a polynomial $f(y) = \sum c_iy^i$ with $c_n > 0$, such that $F(x,y) = \dfrac{f(y)}{x}$ has periodicity $4$, then we have sequence (in the complex sequences, we look at the highest order terms).
\[ a_0 = x, a_1 = y \]
\[ a_2 = \dfrac{\sum_i c_i y^i}{x} = C_2\frac{y^n}{x} + ... \]
\[ a_3 = C_3 \frac{y^{n^2-n}}{x^{n-1}} + ...\]
\[ a_4 = C_4 \dfrac{x*y^{n^3-n^2-n}}{x^{n^2 - n}} + ...\]
So $n^2 - n$ must be 0, which means that $n = 1$ or $n=0$, and $n^3 - n^2 - n$ must be 0, but this is not the case for $n = 1$. So $n=0$.

We can probably employ similar strategies for rational functions.
\section{``Raw'' Idea}

So imagine you have a 3D space, with axis $x,y,z$. And in the space, graph $z = F(x,y)$, $x = F(y,z)$ and $y = F(z,x)$. Then on inputs $a_0 = x$ and $a_1 = y$, then look at the point $(x,y, F(x,y))$. This lies on the surface of $z = F(x,y)$, and the next step is to move that point in the $x$ direction until it intersects the surface defined by $x = F(y,z)$, then we move along the $y$ direction until you intersect surface $y = F(z,x)$, and continue...

Maybe we can characterize the shape of the space? Idk... I prefaced it with the Raw Idea, so I don't feel bad for making you read this jaja.

\end{document}

### 2014-11-17 WaingartenThoughts.tex
fixed typo
added more stuff

@@
 Suppose there was a function $f$ of one variable such that $F(x,y) = \dfrac{f(y)}{x}$ had periodicity 2, then $a_0 = a_2 = x$, $a_1 = y$ and
-\[ a_2 = x = \dfrac{f(x)}{y} \]
-And so $f(x) = xy$, for every $y$, so $f$ is not a function of one variable.
+\[ a_2 = x = \dfrac{f(y)}{x} \]
+And so $f(y) = x^2$, for every $y$, so $f$ is not a function of one variable.
 
@@
 \item $F(x,y) = \dfrac{y}{x}$ with period $6$.
+\item $F(x,y) = \dfrac{cy}{x}$ with period $6$. 
 \item $F(x,y) = x$, with period $2$. 
@@
 We can probably employ similar strategies for rational functions.
+
+\section{Something}
+
+I can show that if $F(x,y) = \dfrac{f(y)}{x}$, where $f$ is degree greater than or equal to 2, then it will not be periodic.
+
+Suppose $f$ is degree $n$, then by looking at the highest degree terms we can let $y_i$ be the highest degree on the $y$ term of the expression. Then
+\[ y_{i+1} = ny_{i} - y_{i-1} \]
+\[ y_0 = 0, y_1 = 1 \]
+So we can show by induction that $y_{i+1} > y_i$, and so the degree of $y$ never goes to 0 (in order for the formula to evaluate to $x$. Its clear for $i = 0$. Suppose it works for some $i$, then 
+\[ y_{i+2} = y_{i+1} + (y_{i+1} - y_{i}) \]
+\[ y_{i+2} > y_{i+1} \]
+following the inductive hypothesis.
+
+Likewise, if $f(y) = \dfrac{P(y)}{Q(y)}$, where $P$ and $Q$ are polynomials of degree $p$ and $q$, then
+\[ y_{i+1} = (p-q)y_{i} - y_{i-1} \]
+So if $p - q \geq 2$, then the function is not periodic.
+
+I also came up with a closed form formula for the highest degree of $y$ at the $i$th iteration by a generating function. 
+So first, 
+\[ Y(x) = \sum y_ix^i = \dfrac{x}{x^2 - nx + 1} \]
+And so we can let $a = \dfrac{n + \sqrt{n^2 - 4}}{2}, b = \dfrac{n - \sqrt{n^2-4}}{2}$, and so 
+\[ y_i = \dfrac{a}{a^2 - 1}(a^i - b^i) \]
+
+Also, one can ask which periodicty can a function have.
+Suppose $F(x,y) = f(y)/x$ where $f$ is a polynomial of degree $1$, since degree $0$ we already solved it.
+Then if we look at the patterns of highest degree terms in $y$, and we have
+\[ y_{i+1} = y_i - y_{i-1} \]
+We know that if the function is periodic, then at some $p$, $y_p = 0$ and $y_{p+1} = 1$.
+This means that $y_{p-1} = -1, y_{p-2} = -1$, then again, $y_{p-3} = 0$.
+Therefore, we know that in the least, $p$ must be a multiple of $3$.
+In addition, since we have a change in parity, then we know that $p$ must be a multiple of $6$.
+In fact, we get $f(y) = y$ gets a periodicity of $6$.
+
+Similarly, if $f(y)$ has highest degree of $y$ with $-1$, then if the function is periodic with periodicity $p$, then $y_p = 0$ and $y_{p+1} = 1$, and so $y_{p-1} = -1$, $y_{p-2} = 1$ and $y_{p-3} = 0$.
+And so the periodicity must be a multiple of $3$.
+
 \section{``Raw'' Idea}

### 2014-11-18 functiontester.py
Adding a simulation
This code has two main methods: buildseq and periodic. buildseq takes in four inputs, the first two terms of the sequence, the function f(y) and the number of iterations, it outputs the recurrent sequence up to n terms as a list. periodic takes in one input a list and outputs the period of the list, if the list is not periodic it returns false. There are also some basic functions f(y).

@@ -1,0 +1,40 @@
+def buildseq(az, ao, function, n):
+    az = az +0.0
+    ao=ao+0.0
+    output=[ao,az]
+    for i in range(n):
+        add = function(ao)/az
+        output.append(add)
+        az=ao
+        ao=add
+    return output
+        
+def periodic(inputlist):
+    a = inputlist[0]
+    b = inputlist[1]
+    l = len(inputlist)
+    i=2
+    while i<l-2:
+        if inputlist[i]==a and inputlist[i+1]==b:
+            return i
+        else:
+            i = i+1
+    return False 
+        
+        
+
+def plusone(x):
+    return x+1
+def squared(x):
+    return x*x
+def plustwo(x):
+    return x+2
+def minusone(x):
+    return x-1
+def plusz(x):
+    return x+.5
+def line(x):
+    return 3*x+1
+b= buildseq(1,1,plustwo,400)
+#print b
+print periodic(b)

### 2014-11-18 functiontester.py
Fixed a typo

@@ -1,7 +1,7 @@
 def buildseq(az, ao, function, n):
     az = az +0.0
     ao=ao+0.0
-    output=[ao,az]
+    output=[az,ao]
     for i in range(n):
         add = function(ao)/az
         output.append(add)

### 2014-11-18 functiontester.py
Adding more functions/testing up to 40,000

@@ -35,6 +35,12 @@ def plusz(x):
     return x+.5
 def line(x):
     return 3*x+1
-b= buildseq(1,1,plustwo,400)
+def one(x):
+    return 1
+def identity(x):
+    return x
+def reciprocal(x):
+    return 1/x
+b= buildseq(4,3,minusone,40000)
 #print b
 print periodic(b)

### 2014-11-19 WaingartenThoughts.tex
fixed wrong statements

--- 2014-11-14 WaingartenThoughts.tex
@@
 \item $F(x,y) = \dfrac{y}{x}$ with period $6$.
+\item $F(x,y) = \dfrac{y+1}{x}$ with period $5$.
+\item $F(x,y) = \dfrac{cy}{x}$ with period $6$. 
 \item $F(x,y) = x$, with period $2$. 
@@
 We can probably employ similar strategies for rational functions.
+
+\section{Something}
+
+I can show that if $F(x,y) = \dfrac{f(y)}{x}$, where $f$ is degree greater than or equal to 2, then it will not be periodic.
+
+Suppose $f$ is degree $n$, then by looking at the highest degree terms we can let $y_i$ be the highest degree on the $y$ term of the expression. Then
+\[ y_{i+1} \geq ny_{i} - y_{i-1} \]
+\[ y_0 = 0, y_1 = 1 \]
+So we can show by induction that $y_{i+1} > y_i$, and so the degree of $y$ never goes to 0 (in order for the formula to evaluate to $x$. Its clear for $i = 0$. Suppose it works for some $i$, then 
+\[ y_{i+2} \geq y_{i+1} + (y_{i+1} - y_{i}) \]
+\[ y_{i+2} > y_{i+1} \]
+following the inductive hypothesis.
+
+Likewise, if $f(y) = \dfrac{P(y)}{Q(y)}$, where $P$ and $Q$ are polynomials of degree $p$ and $q$, then
+\[ y_{i+1} \geq (p-q)y_{i} - y_{i-1} \]
+So if $p - q \geq 2$, then the function is not periodic.
+
 \section{``Raw'' Idea}

### 2014-11-21 perrysthoughts.tex
Added stuff on ratios of Linear polynomials
Showed there are only 3 ratios of linear polynomials that have period 3.

\title{Perry's Thoughts}
\date{}

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsthm}

\begin{document}
\maketitle
\section{How to Deal with 0}
In order for our rules to be complete we must have some method for dealing with $0$. In order to handle this we will include an inverse for $0$ which we will write as $0^{-1}$. So we have 
\begin{align*}
0*0^{-1} =1
\end{align*}
We will treat $0^{-1}$ as an variable, that is related to the reals only by the above relation. We are essentially ignoring $0$ and/or when working with our equations we are assuming that the denominator is never $0$.

\section{Question 4} 
I hypothesize that $f(y) = by+c, b \neq 0$ is periodic for $c = 1, b=1$ with period 5, and is not periodic when $c \neq 0,1$ or when $b \neq 1$. That is the only linear polynomials which are periodic are $y+1$ and $by$ for $ b \neq 0$. 
\begin{proof}
If $c=1$ suppose we have $a_0 =x, a_1 =y$, we want to show that $a_5=a_0$ and $a_6=a_1$. Well 
\begin{equation*}
a_2 = \frac{f(a_1)}{a_0} = \frac{ a_1 +1}{a_0} = \frac{y+1}{x},
\end{equation*}
and so 
\begin{equation*}
a_3 = \frac{a_2+1}{a_1} = \frac{ \frac{y+1}{x} +1}{y} = \frac{x+y+1}{xy},
\end{equation*}
so
\begin{equation*}
a_4 = \frac{a_3 +1}{a_2} = \frac{ \frac{y+1+x}{xy} +1}{\frac{y+1}{x}} = \frac{x+y+1+xy}{y(y+1)},
\end{equation*}
giving us 
\begin{align*}
a_5 &=\frac{a_4+1}{a_3} = \left(\frac{x+y+1+xy}{y(y+1)} +1\right)\left( \frac{xy}{x+y+1} \right)= \frac{ x(x+y+1) + xxy + xy(y+1)}{(y+1)(x+y+1)} \\
&= \frac{x^2(y+1) + x(y+1) + xy(y+1)}{(y+1)(x+y+1)} = \frac{x(x+y+1)}{x+y+1} = x = a_0.
\end{align*}
So finally we calculate $a_6$ and find 
\begin{align*}
a_6 = \frac{a_5 +1}{a_4} = (x+1)\left( \frac{y(y+1)}{x+y+1+xy} \right) = \frac{xy^2 + xy+y^2+y}{x+y+1+xy} =y =a_1
\end{align*}
Therefore $f(y)=y+1$ is periodic with period 5 as desired. 
\end{proof}
By numerical simulation we have checked that if $f(y) = y+2$ or $f(y)=y-1$ are periodic they have period longer than 40,000.

\section{Linear Rational Functions}
In this section we consider $F(x,y)$ of the form
\begin{equation}
\label{rationallinear}
F(x,y) = \frac{b_1 x+b_2 y + b_3}{c_1 x + c_2 y+ c_3},
\end{equation}
and ask the questions given $n$ for what choice of $b_i$ and $c_i$ will we produce a function with a period $n$ and for what $n$'s can we do this?

\begin{proposition} 
If $F(x,y)$ is of the form in \ref{rationallinear} and the recurrence relation it produces has period $3$ then $F$ is one of three functions. In particular we can have 
\begin{align*}
F(x,y) &= -x-y \\
F(x,y) &= \left( \frac{1}{2} +\frac{i\sqrt{3}}{2} \right) x + \left( \frac{1}{2} -\frac{i\sqrt{3}}{2} \right) y \\
F(x,y) &= \left( \frac{1}{2} -\frac{i\sqrt{3}}{2} \right) x + \left( \frac{1}{2} +\frac{i\sqrt{3}}{2} \right) y
\end{align*}
\end{proposition}
\begin{proof}
In order for $F(x,y)$ to induce a recurrence relation with period $3$ we must have
\begin{equation*}
\left( (c_1 x + c_2 y +c_3) c_1 y + c_2 (b_1 x + b_2 y + b_3) + c_3(c_1 x + c_2 y +c_3) \right) x = (c_1 x + c_2 y + c_3) b_1 y + b_2(b_1 x + b_2 y + b_3) + b_3 (c_1 x = c_2 y + c_3),
\end{equation*}
which we obtain from writing down $a_3=a_0$ in terms of $x$ and $y$ and clearing denominators. If we multiply this expression out we get 
\begin{equation*}
c_1^2 x^2 y + c_2 c_1 y^2 x + (c_3 c_1 + c_2 b_2 + c_3 c_2)xy + (c_2b_1 + c_3 c_1) x^2 + (b_3 + c_3)x = c_1 b_1 xy + c_2 b_1 y^2 + c_3 b_1 y + (b_2 b_1 + b_3 c_1)x + (b_2^2 +b_3 c_2)y + b_2 b_3 + b_3 c_3.
\end{equation*}
Because this relation must hold for arbitrary $x$ and $y$ we know that terms with the same exponents for $x$ and $y$ must cancel. So for instance we must have 
\begin{equation*}
c_1^2 x^2 y = 0, 
\end{equation*}
and so we must have $c_1=0$. We can do this for terms of each order and find the following 5 relations for the coefficients 
\begin{align}
\label{fiverelations}
c_2(b_2 + c_3) =0 \\
c_2 b_1 = 0 \\
b_3 + c_3 = b_2 b_1 \\
c_3 b_1 + b_2^2 + b_3 c_2 =0 \\
b_3(b_2 + c_3) = 0. 
\end{align}
Suppose that $c_2 =0$, then $F$ is of the form 
\begin{equation*}
F(x,y) = \frac{ b_1 x + b_2 y + b_3}{c_3}.
\end{equation*}
Therefore we must have 
\begin{equation*}
c_3^2 x = b_1 c_3 y + b_2 (b_1 x + b_2 y + b_3) + b_3,
\end{equation*}
which gives us a new family of relations 
\begin{align*}
b_2 b_1 = c_3^2 \\
c_3 b_1 + b_2^2 =0.
\end{align*}
Combining these two gives us 
\begin{equation*}
c_3^3 + b_2^3 = 0, 
\end{equation*}
which has three solutions $c_3 = -b_2$ and $c_3 = \frac{1}{2} ( b_2 \pm i\sqrt{3}b_2)$. Note that $c_3 = -b_2$ implies that we must have $b_1=b_2$ which gives us $F(x,y) = -x -y$. It is easy to check that this is in fact periodic with period 3. On the other hand $c_3 = \frac{1}{2} ( b_2 \pm i\sqrt{3}b_2)$ implies that $b_1 = \frac{1}{2} ( -b_2 \pm i\sqrt{3}b_2)$, which gives us 
\begin{align*}
F(x,y) &= \left( \frac{1}{2} -\frac{i\sqrt{3}}{2} \right) x + \left( \frac{1}{2} +\frac{i\sqrt{3}}{2} \right) y \\
F(x,y) &= \left( \frac{1}{2} +\frac{i\sqrt{3}}{2} \right) x + \left( \frac{1}{2} -\frac{i\sqrt{3}}{2} \right) y.
\end{align*}
This exhausts the possibilities when $c_2=0$ so let us asssume otherwise. Then based on the relations \ref{fiverelations} we must have 
\begin{equation*}
b_1 = 0,
\end{equation*}
and so $F(x,y)$ takes the form 
\begin{equation*}
F(x,y) = \frac{b_2 y + b_3}{c_2 y + c_3}.
\end{equation*}
Therefore if $a_3 = a_0$ we must have that 
\begin{equation*}
x = \frac{ b_2^2 y + b_2b_3 +b_3(c_2 y + c_3)}{c_2 b_2 y + c_2 b_3 + c_3 c_2 y + c_3^2},
\end{equation*}
but the left hand side depends only on $x$ and the right hand side depends only on $y$. This relation cannot hold for arbitrary $x,y$ and so we cannot have such $F$. Therefore we must have $c_2=0$ and so the only $F$ with period 3 are the ones we have given. 
\end{proof}
\end{document}

### 2014-11-21 perrysthoughts.tex
Fixed typo
added sentence on period 2

@@
 
+It is somewhat obvious that $F(x,y)=x$ is the only ratio of linear functions that has period 2, however for larger $n$ the question and answer are slightly more interesting. 
 \begin{proposition} 
@@
 \end{align*}
-This exhausts the possibilities when $c_2=0$ so let us asssume otherwise. Then based on the relations \ref{fiverelations} we must have 
+It is also easy to check that these two $F$ have period 3. This exhausts the possibilities when $c_2=0$ so let us asssume otherwise. Then based on the relations \ref{fiverelations} we must have 
 \begin{equation*}

### 2014-11-23 fermithoughts.tex
adding fermi thoughts

--- 2014-11-21 perrysthoughts.tex
@@
-\title{Perry's Thoughts}
+\title{Fermi's Thoughts}
 \date{}
@@
 \maketitle
-\section{How to Deal with 0}
-In order for our rules to be complete we must have some method for dealing with $0$. In order to handle this we will include an inverse for $0$ which we will write as $0^{-1}$. So we have 
-\begin{align*}
-0*0^{-1} =1
-\end{align*}
-We will treat $0^{-1}$ as an variable, that is related to the reals only by the above relation.
-We are essentially ignoring $0$ and/or when working with our equations we are assuming that the denominator is never $0$.
 
-\section{Question 4} 
-I hypothesize that $f(y) = by+c, b \neq 0$ is periodic for $c = 1, b=1$ with period 5, and is not periodic when $c \neq 0,1$ or when $b \neq 1$.
-That is the only linear polynomials which are periodic are $y+1$ and $by$ for $ b \neq 0$.
-\begin{proof}
-If $c=1$ suppose we have $a_0 =x, a_1 =y$, we want to show that $a_5=a_0$ and $a_6=a_1$. Well 
-\begin{equation*}
-a_2 = \frac{f(a_1)}{a_0} = \frac{ a_1 +1}{a_0} = \frac{y+1}{x},
-\end{equation*}
-and so 
-\begin{equation*}
-a_3 = \frac{a_2+1}{a_1} = \frac{ \frac{y+1}{x} +1}{y} = \frac{x+y+1}{xy},
-\end{equation*}
-so
-\begin{equation*}
-a_4 = \frac{a_3 +1}{a_2} = \frac{ \frac{y+1+x}{xy} +1}{\frac{y+1}{x}} = \frac{x+y+1+xy}{y(y+1)},
-\end{equation*}
-giving us 
-\begin{align*}
-a_5 &=\frac{a_4+1}{a_3} = \left(\frac{x+y+1+xy}{y(y+1)} +1\right)\left( \frac{xy}{x+y+1} \right)= \frac{ x(x+y+1) + xxy + xy(y+1)}{(y+1)(x+y+1)} \\
-&= \frac{x^2(y+1) + x(y+1) + xy(y+1)}{(y+1)(x+y+1)} = \frac{x(x+y+1)}{x+y+1} = x = a_0.
-\end{align*}
-So finally we calculate $a_6$ and find 
-\begin{align*}
-a_6 = \frac{a_5 +1}{a_4} = (x+1)\left( \frac{y(y+1)}{x+y+1+xy} \right) = \frac{xy^2 + xy+y^2+y}{x+y+1+xy} =y =a_1
-\end{align*}
-Therefore $f(y)=y+1$ is periodic with period 5 as desired. 
-\end{proof}
-By numerical simulation we have checked that if $f(y) = y+2$ or $f(y)=y-1$ are periodic they have period longer than 40,000.
+\section{Period 2}
 
-\section{Linear Rational Functions}
-In this section we consider $F(x,y)$ of the form
-\begin{equation}
-\label{rationallinear}
-F(x,y) = \frac{b_1 x+b_2 y + b_3}{c_1 x + c_2 y+ c_3},
-\end{equation}
-and ask the questions given $n$ for what choice of $b_i$ and $c_i$ will we produce a function with a period $n$ and for what $n$'s can we do this?
+\section{Period 3}
 
-\begin{proposition} 
-If $F(x,y)$ is of the form in \ref{rationallinear} and the recurrence relation it produces has period $3$ then $F$ is one of three functions. In particular we can have 
-\begin{align*}
-F(x,y) &= -x-y \\
-F(x,y) &= \left( \frac{1}{2} +\frac{i\sqrt{3}}{2} \right) x + \left( \frac{1}{2} -\frac{i\sqrt{3}}{2} \right) y \\
-F(x,y) &= \left( \frac{1}{2} -\frac{i\sqrt{3}}{2} \right) x + \left( \frac{1}{2} +\frac{i\sqrt{3}}{2} \right) y
-\end{align*}
-\end{proposition}
-\begin{proof}
-In order for $F(x,y)$ to induce a recurrence relation with period $3$ we must have
-\begin{equation*}
-\left( (c_1 x + c_2 y +c_3) c_1 y + c_2 (b_1 x + b_2 y + b_3) + c_3(c_1 x + c_2 y +c_3) \right) x = (c_1 x + c_2 y + c_3) b_1 y + b_2(b_1 x + b_2 y + b_3) + b_3 (c_1 x = c_2 y + c_3),
-\end{equation*}
-which we obtain from writing down $a_3=a_0$ in terms of $x$ and $y$ and clearing denominators. If we multiply this expression out we get 
-\begin{equation*}
-c_1^2 x^2 y + c_2 c_1 y^2 x + (c_3 c_1 + c_2 b_2 + c_3 c_2)xy + (c_2b_1 + c_3 c_1) x^2 + (b_3 + c_3)x = c_1 b_1 xy + c_2 b_1 y^2 + c_3 b_1 y + (b_2 b_1 + b_3 c_1)x + (b_2^2 +b_3 c_2)y + b_2 b_3 + b_3 c_3.
-\end{equation*}
-Because this relation must hold for arbitrary $x$ and $y$ we know that terms with the same exponents for $x$ and $y$ must cancel. So for instance we must have 
-\begin{equation*}
-c_1^2 x^2 y = 0, 
-\end{equation*}
-and so we must have $c_1=0$. We can do this for terms of each order and find the following 5 relations for the coefficients 
-\begin{align}
-\label{fiverelations}
-c_2(b_2 + c_3) =0 \\
-c_2 b_1 = 0 \\
-b_3 + c_3 = b_2 b_1 \\
-c_3 b_1 + b_2^2 + b_3 c_2 =0 \\
-b_3(b_2 + c_3) = 0. 
-\end{align}
-Suppose that $c_2 =0$, then $F$ is of the form 
-\begin{equation*}
-F(x,y) = \frac{ b_1 x + b_2 y + b_3}{c_3}.
-\end{equation*}
-Therefore we must have 
-\begin{equation*}
-c_3^2 x = b_1 c_3 y + b_2 (b_1 x + b_2 y + b_3) + b_3,
-\end{equation*}
-which gives us a new family of relations 
-\begin{align*}
-b_2 b_1 = c_3^2 \\
-c_3 b_1 + b_2^2 =0.
-\end{align*}
-Combining these two gives us 
-\begin{equation*}
-c_3^3 + b_2^3 = 0, 
-\end{equation*}
-which has three solutions $c_3 = -b_2$ and $c_3 = \frac{1}{2} ( b_2 \pm i\sqrt{3}b_2)$.
-Note that $c_3 = -b_2$ implies that we must have $b_1=b_2$ which gives us $F(x,y) = -x -y$.
-It is easy to check that this is in fact periodic with period 3.
-On the other hand $c_3 = \frac{1}{2} ( b_2 \pm i\sqrt{3}b_2)$ implies that $b_1 = \frac{1}{2} ( -b_2 \pm i\sqrt{3}b_2)$, which gives us
-\begin{align*}
-F(x,y) &= \left( \frac{1}{2} -\frac{i\sqrt{3}}{2} \right) x + \left( \frac{1}{2} +\frac{i\sqrt{3}}{2} \right) y \\
-F(x,y) &= \left( \frac{1}{2} +\frac{i\sqrt{3}}{2} \right) x + \left( \frac{1}{2} -\frac{i\sqrt{3}}{2} \right) y.
-\end{align*}
-This exhausts the possibilities when $c_2=0$ so let us asssume otherwise. Then based on the relations \ref{fiverelations} we must have 
-\begin{equation*}
-b_1 = 0,
-\end{equation*}
-and so $F(x,y)$ takes the form 
-\begin{equation*}
-F(x,y) = \frac{b_2 y + b_3}{c_2 y + c_3}.
-\end{equation*}
-Therefore if $a_3 = a_0$ we must have that 
-\begin{equation*}
-x = \frac{ b_2^2 y + b_2b_3 +b_3(c_2 y + c_3)}{c_2 b_2 y + c_2 b_3 + c_3 c_2 y + c_3^2},
-\end{equation*}
-but the left hand side depends only on $x$ and the right hand side depends only on $y$.
-This relation cannot hold for arbitrary $x,y$ and so we cannot have such $F$.
-Therefore we must have $c_2=0$ and so the only $F$ with period 3 are the ones we have given.
-\end{proof}
+\section{Period 4}
+
 \end{document}

### 2014-11-23 fermithoughts.tex
updated fermi thoughts, finished with f(y)/x for periods up to 4

@@
 
-\section{Period 2}
+\section{Period 2 for $F(x,y)$}
 
-\section{Period 3}
+Suppose we have period 2. Then our sequence is $x,y,x,y,\dots$, and in particular, we know that $F(x,y) = x$ must hold by looking at the third term.
 
-\section{Period 4}
+Since this equality holds, that is the only possible value for $F(x,y)$. Also, since $F(x,y)$ is not of the form $f(y)/x$, this shows that there are no period 2 sequences generated by $f(y)/x$.
+
+\section{Period 3 for $f(y)/x$, $y$ is any function}
+
+Suppose we have period 3. Then our sequence is
+\[ x,y,f(y)/x,x,y,f(y)/x,\dots\]
+and from looking at the fourth and fifth terms, we get the following two equations
+\begin{align*}
+x &= f(f(y)/x)/y\\
+y &= xf(x)/f(y)\\
+\end{align*}
+Note that the second equation tells us that $yf(y) = xf(x)$, and this must hold true for any choice of $x$ and $y$, and so this mean that $yf(y) = xf(x) = c$ for some constant $c$.
+This tells us that $f(y)$ must be of the form $c/y$.
+
+So $\frac{c}{xy}$ is the only function of the form $f(y)/x$ with period 3.
+\section{Period 4 for $f(y)/x$, $f(y)$ is a polynomial}
+
+Assume $f(y)$ is a nonconstant polynomial. Suppose we have period 4. We show that we will get a contradiction.
+
+Our sequence is
+\[ x,y,\frac{f(y)}{x},\frac{f(f(y)/x)}{y},x,y,\frac{f(y)}{x},\frac{f(f(y)/x)}{y},\dots\]
+
+Look at the sixth term, and note that the following relation must hold
+\[ y = \frac{f(x)y}{f(f(y)/x)} \]
+or equivalently if $y /neq 0$,
+\[ f(f(y)/x) = f(x) \]
+Now fix $x = 1$. Then we get 
+\[ f(f(y)) = f(1) = c \]
+
+Note that since this equation must hold, and since $f(y)$ can take on infinitely many values (this is true of any nonconstant polynomial), we have infinitely many solutions to $f(f(y)) = f(1)$.
+In particular, $f(f(y)) - f(1)$ is a polynomial in $f(y)$ with infinitely many distinct roots.
+This is a contradiction.
+
+So for this case to work, $f(y)$ must be a constant.
 

### 2014-11-24 draft.tex
added intro, fixed smal typo in fermithoughts

\title{A Recurrence}
\author{
  Perry Kleinhenz \and
  Fermi Ma \and
  Erik Waingarten
}
\date{\today}

\documentclass[12pt]{article}
\usepackage{amsmath}

\begin{document}
\maketitle

\section{Introduction}
\emph{Written by Erik Waingarten}

In this paper, we will study recurrences with \textit{memory two}. By memory two, we mean that the sequence can be described by a recurrence where a certain number depends on the previous two numbers. We can define a sequence $a_0, a_1, a_2, \dots$ recursively using a function $F(x,y)$ of two variables, where we assign
\[ a_{n+1} = F(a_n, a_{n-1}) \]
Note that this is the ultimate generalization of recurrences which depends on the previous two terms. The famous Fibonacci sequence fits this mold: we can let $F(x,y) = x + y$, and the recurrence will yield
\[ a_{n+1} = a_n + a_{n-1} \]
If we let $a_0 = a_1 = 1$, we get the Fibonacci sequence. In this paper, we will focus on the properties that arise out of different definitions of the functions $F(x,y)$, independent of the intial terms. So usually, we will let $a_0 = x$ and $a_1 = y$, and we assume that $x$ and $y$ can take on any values. We will say that a recursive definition is \textit{periodic} if, with indeterminate intiail values $a_0 = x$ and $a_1 = y$, there is an integer $n>0$ such that $a_n = x$ and $a_{n+1} = y$. The \emph{period} is the smallest such $n$.

We can compute some simple examples to promote our search. 
\begin{itemize}
\item $F(x,y) = y$: $x, y, x, y, x, \dots$, so we get period $2$.
\item $F(x,y) = \dfrac{1}{xy}$: $x, y, \dfrac{1}{xy}, x, y, \dots$, so we get period $3$.
\item $F(x,y) = \dfrac{1}{x}$: $x, y, \dfrac{1}{x}, \dfrac{1}{y}, x, y, \dots$, so we get period $4$.
\end{itemize}

There are some functions $F(x,y)$ such as the one generating the Fibonacci sequence which do not yield periodic sequences. One can ask, is there a simple test that determines whether a function yields a periodic sequence? Can we characterize the such functions? What are the possible periods?

These are questions that we hope to answer.

\end{document}

### 2014-11-24 draft.tex
started second section

@@
 \usepackage{amsmath}
+\usepackage{amsthm}
+
+\newtheorem{proposition}{Proposition}
 
@@
 
+\section{The case of $F(x,y) = f(y)/x$}
+
+We begin by studying the special case where $F(x,y) = \dfrac{f(y)}{x}$. So that means that the sequences are defined by the relation
+\begin{equation}
+\label{eq:firstcase}
+a_{n+1} = \dfrac{f(a_{n-1})}{a_n}
+\end{equation}
+In the introduction, we've already seen two functions in this form that are periodic. Namely, $f(y) = 1$ and $f(y) = \frac{1}{y}$.
+
+\begin{proposition}
+The only possible $f$ which yields a sequence of period $3$ according to the recurrence in Equation~\ref{eq:firstcase} is $f(y) = \dfrac{c}{xy}$.
+\end{proposition}
+
+\begin{proof}
+We can look at the first few values of the sequence:
+\[ x, y, \dfrac{f(y)}{x}, x, y, \dots \]
+By looking at $a_4$, observe that
+\[ y = \dfrac{xf(x)}{f(y)} \]
+and so,
+\[ y f(y) = x f(x) \]
+Fix $x = 1$. Then we have $y f(y) = f(1)$, and so $f(y) = \dfrac{c}{y}$, where $c$ is any constant .
+\end{proof}
+
+Likewise, we can do a similar analysis for period $4$. 
+\begin{proposition}
+The only possible $f$ (polynomial) which yields a sequence of period 4 according to the recurrence in Equation~\ref{eq:firstcase} is $f(y) = c$. 
+\end{proposition}
+
+\begin{proof}
+First, we can easily check that these functions yield a sequence with period $4$. If we had any function $f$ which yielded a sequence with period $4$, then 
+\[ x, y, \dfrac{f(y)}{x}, \dfrac{f(f(y)/x)}{y}, x, y, \dots \]
+And by looking at $a_6$, observe
+\[ y = \dfrac{yf(x)}{f(f(y)/x)} \]
+and so 
+\[ f(f(y)/x) = f(x) \]
+If we fix $x = 1$, then we have
+\[ f(f(y)) = f(1) \]
+Which means that $f(f(y))$ is a constant for every $y$.
+And so since $f(y)$ is non-constant, it will take on infinitely many values, which means that $f(y) - f(1)$ is also a polynomial with infinitely many roots, and so $f(y) = f(1)$.
+\end{proof}
+
 \end{document}

### 2014-11-25 draft.tex
Some edits to first two sections, adding section 3

--- 2014-11-24 draft.tex
@@
 
+\section{The case of $F(x,y) = f(y)/x$}
+\emph{Written by Erik Waingarten, edited by Perry Kleinhenz and Fermi Ma}
+
+We begin by considering the special case where 
+\begin{equation}\label{eq:firstcase}
+F(x,y) = \dfrac{f(y)}{x}
+\end{equation}. In other words, the sequences are defined by the relation
+\begin{equation*}
+a_{n+1} = \dfrac{f(a_{n-1})}{a_n}
+\end{equation*}
+In the introduction, we've already seen two functions of this form that are periodic. Namely, $f(y) = 1$ and $f(y) = \frac{1}{y}$.
+
+\begin{proposition}
+If $F$ is of the form in equation ~\ref{eq:firstcase} and has period 3, then $F(x,y) = \dfrac{c}{xy}$.
+\end{proposition}
+
+\begin{proof}
+Consider the first 4 terms of the :
+\begin{equation*}
+x, y, \dfrac{f(y)}{x}, x, y, \dots 
+\end{equation*}
+We note that $a_4=y$ and using the recurrence relation we find that 
+\begin{equation*}
+y = \dfrac{xf(x)}{f(y)},
+\end{equation*}
+and so,
+\begin{equation*} 
+y f(y) = x f(x).
+\end{equation*}
+Now if we fix $x = 1$, we have $y f(y) = f(1)$, and so $f(y) = \dfrac{c}{y}$, where $c$ is some constant .
+\end{proof}
+
+We can do a similar analysis for period $4$.
+\begin{proposition}
+f $F$ is of the form in equation ~\ref{eq:firstcase} and has period 4 and $f$ is a polynomial then $f(y) = c$. 
+\end{proposition}
+
+\begin{proof}
+It is easy to check that these functions yield a sequence with period $4$, as they would form a sequence $x,y, \frac{c}{x}, \frac{c}{y}, x, y, \ldots$.
+
+Now suppose we have some non constant polynomial  $f$ that produces a sequence with period $4$. The  the first few terms of the sequence are 
+\begin{equation*}
+x, y, \dfrac{f(y)}{x}, \dfrac{f(f(y)/x)}{y}, x, y, \dots \, .
+\end{equation*}
+We note that $a_5 =y$ and using the recurrence relation we find that 
+\begin{equation*}
+ y = \dfrac{yf(x)}{f(f(y)/x)}, 
+ \end{equation*}
+simplifying gives us  
+\begin{equation*}
+ f(f(y)/x) = f(x).
+\end{equation*}
+If we fix $x = 1$, we have
+\begin{equation*}
+f(f(y)) = f(1). 
+\end{equation*}
+This means that $f(f(y))$ is a constant for every $y$.
+If we let $z=f(y)$ then we can see that $f(z)-f(1)$ is a polynomial in $z$ and has infinitely many roots.
+This is a contradiction as polynomials can only have finitely many roots.
+Therefore $f$ must be a constant.
+\end{proof}
+
+\section{Rational/Linear F}
+In this section we consider an $F$ which is a rational function composed of arbitrary linear functions. That is 
+\begin{equation}
+\label{rationallinear}
+F(x,y) = \frac{ b_1 x + b_2 y + b_3}{ c_1 x+ c_2 y + c_3}
+\end{equation}
+Recall that our recurrence is $a_{n+1} = F( a_{n-1}, a_n)$. We can write out the first few terms of the sequence with arbitrary starting values $x,y$
+\begin{align}
+a_0 &= x \\ 
+a_1 &=y \\
+a_2 &= \frac{ b_1 x + b_2 y + b_3}{ c_1 x+ c_2 y + c_3}\\
+\label{athree}a_3 &= \frac{(c_1 x+ c_2 y + c_3) b_1 y + b_2 (b_1 x + b_2 y + b_3)+ b_3(c_1 x+ c_2 y + c_3)}{ (c_1 x+ c_2 y + c_3)c_1 y+ c_2 (b_1 x + b_2 y + b_3) + c_3(c_1 x+ c_2 y + c_3)} \\
+\vdots
+\end{align}
+These expressions get complicated very quickly, but we can use them to classify the periodic behavior of these functions.
+
+It is somewhat obvious that $F(x,y)=x$ is the only ratio of linear functions that has period 2, however for larger $n$ the question and answer are slightly more interesting. 
+\begin{proposition} 
+If $F(x,y)$ is of the form in Equation \ref{rationallinear} and the recurrence relation it produces has period $3$ then $F$ is one of three following functions:
+\begin{align*}
+F(x,y) &= -x-y \\
+F(x,y) &= \left( \frac{1}{2} +\frac{i\sqrt{3}}{2} \right) x + \left( \frac{1}{2} -\frac{i\sqrt{3}}{2} \right) y \\
+F(x,y) &= \left( \frac{1}{2} -\frac{i\sqrt{3}}{2} \right) x + \left( \frac{1}{2} +\frac{i\sqrt{3}}{2} \right) y.
+\end{align*}
+\end{proposition}
+\begin{proof}
+In order for $F(x,y)$ to induce a recurrence relation with period $3$ we must have $a_3=a_0$. So using the expression in Equation \ref{athree} we must have 
+\begin{align*}
+\left( (c_1 x + c_2 y +c_3) c_1 y + c_2 (b_1 x + b_2 y + b_3) + c_3(c_1 x + c_2 y +c_3) \right) x = \\(c_1 x + c_2 y + c_3) b_1 y + b_2(b_1 x + b_2 y + b_3) + b_3 (c_1 x = c_2 y + c_3),
+\end{align*}
+If we multiply this expression out we get 
+\begin{align*}
+c_1^2 x^2 y + c_2 c_1 y^2 x + (c_3 c_1 + c_2 b_2 + c_3 c_2)xy + (c_2b_1 + c_3 c_1) x^2 + (b_3 + c_3)x = \\ c_1 b_1 xy + c_2 b_1 y^2 + c_3 b_1 y + (b_2 b_1 + b_3 c_1)x + (b_2^2 +b_3 c_2)y + b_2 b_3 + b_3 c_3.
+\end{align*}
+Because this relation must hold for arbitrary $x$ and $y$ we know that terms with the same exponents for $x$ and $y$ must cancel. So for instance we must have 
+\begin{equation*}
+c_1^2 x^2 y = 0, 
+\end{equation*}
+and so we must have $c_1=0$. We can do this for terms of each order and find the following 5 relations for the coefficients 
+\begin{align}
+\label{fiverelations}
+c_2(b_2 + c_3) =0 \\
+c_2 b_1 = 0 \\
+b_3 + c_3 = b_2 b_1 \\
+c_3 b_1 + b_2^2 + b_3 c_2 =0 \\
+b_3(b_2 + c_3) = 0. 
+\end{align}
+Suppose that $c_2 =0$, then $F$ is of the form 
+\begin{equation*}
+F(x,y) = \frac{ b_1 x + b_2 y + b_3}{c_3}.
+\end{equation*}
+Therefore we must have 
+\begin{equation*}
+c_3^2 x = b_1 c_3 y + b_2 (b_1 x + b_2 y + b_3) + b_3,
+\end{equation*}
+which gives us a new family of relations 
+\begin{align*}
+b_2 b_1 = c_3^2 \\
+c_3 b_1 + b_2^2 =0.
+\end{align*}
+Combining these two gives us 
+\begin{equation*}
+c_3^3 + b_2^3 = 0, 
+\end{equation*}
+which has three solutions $c_3 = -b_2$ and $c_3 = \frac{1}{2} ( b_2 \pm i\sqrt{3}b_2)$.
+Note that $c_3 = -b_2$ implies that we must have $b_1=b_2$ which gives us $F(x,y) = -x -y$.
+It is easy to check that this is in fact periodic with period 3.
+On the other hand $c_3 = \frac{1}{2} ( b_2 \pm i\sqrt{3}b_2)$ implies that $b_1 = \frac{1}{2} ( -b_2 \pm i\sqrt{3}b_2)$, which gives us
+\begin{align*}
+F(x,y) &= \left( \frac{1}{2} -\frac{i\sqrt{3}}{2} \right) x + \left( \frac{1}{2} +\frac{i\sqrt{3}}{2} \right) y \\
+F(x,y) &= \left( \frac{1}{2} +\frac{i\sqrt{3}}{2} \right) x + \left( \frac{1}{2} -\frac{i\sqrt{3}}{2} \right) y.
+\end{align*}
+It is also easy to check that these two $F$ have period 3. This exhausts the possibilities when $c_2=0$ so let us asssume otherwise. Then based on the relations \ref{fiverelations} we must have 
+\begin{equation*}
+b_1 = 0,
+\end{equation*}
+and so $F(x,y)$ takes the form 
+\begin{equation*}
+F(x,y) = \frac{b_2 y + b_3}{c_2 y + c_3}.
+\end{equation*}
+Therefore if $a_3 = a_0$ we must have that 
+\begin{equation*}
+x = \frac{ b_2^2 y + b_2b_3 +b_3(c_2 y + c_3)}{c_2 b_2 y + c_2 b_3 + c_3 c_2 y + c_3^2},
+\end{equation*}
+but the left hand side depends only on $x$ and the right hand side depends only on $y$.
+This relation cannot hold for arbitrary $x,y$ and so we cannot have such $F$.
+Therefore we must have $c_2=0$ and so the only $F$ with period 3 are the ones we have given.
+\end{proof}
+
 \end{document}

### 2014-11-25 draft.tex
Adding period 5 to section 2

@@
 
+We can also perform this analysis for period $5$  
+\begin{proposition}
+If $F$ is of the form in equation ~\ref{eq:firstcase} and has period 4 and $f$ is a polynomial then $f(y) = cy+c^2$
+\end{proposition}
+\begin{proof}
+First we must show that $a_5=a_0$ and $a_6=a_1$. Well 
+\begin{equation*}
+a_2 = \frac{cy+c^2}{x},
+\end{equation*}
+and so 
+\begin{equation*}
+a_3 = \frac{ c \frac{cy+c^2}{x} +c^2}{y} = \frac{c^2y + c^3+c^3x}{xy},
+\end{equation*}
+so
+\begin{equation*}
+a_4  = \frac{c \frac{cy + c^2+c^2x}{xy} +c^2}{\frac{cy+c^2}{x}} = \frac{c^2y+c^2+c^2x+c^2xy}{y(cy+c^2)} = \frac{c(c+x)}{y},
+\end{equation*}
+giving us 
+\begin{align*}
+a_5 &=\left(c \frac{c(c+x)}{y} + c^2\right) \frac{xy}{c^2y+c^3+c^3x} = \frac{c^2y+c^3+c^3x}{y} \frac{xy}{c^2y+c^3+c^3x}= x.
+\end{align*}
+We can finally calculate $a_6$ and find 
+\begin{align*}
+a_6 = (cx + c^2) \frac{y}{cx+c^2} = y
+\end{align*}
+Therefore $f(y)=cy+c^2$ is periodic with period 5 as desired. 
+\end{proof}
+
 \section{Rational/Linear F}

### 2014-11-25 draft.tex
Edits to Period 5 in section 2

@@
 \begin{proposition}
-If $F$ is of the form in equation ~\ref{eq:firstcase} and has period 4 and $f$ is a polynomial then $f(y) = cy+c^2$
+If $F$ is of the form in equation ~\ref{eq:firstcase} and has period 5 and $f$ is a polynomial then $f(y) = cy+c^2$. 
 \end{proposition}
@@
 Therefore $f(y)=cy+c^2$ is periodic with period 5 as desired.
+Now we would like to show that all polynomial $f$ must be of this form.
+So if we consider an arbitrary $f$ we know that the first few terms of the sequence will be
+\begin{equation*}
+x,y, \frac{f(y)}{x}, \frac{f(f(y)/x)}{y}, \frac{xf( f(f(y)/x)/y)}{f(y)}, x, y, \ldots
+\end{equation*}
+For ease of notation we will write $A=f(y)$
 \end{proof}

### 2014-11-25 draft.tex
Finished proof for Period 5 in section 2

@@
 \end{equation*}
-For ease of notation we will write $A=f(y)$
+Now using the recurrence relation and setting $a_5=a$ and $a_6=y$, we obtain the relations
+\begin{align*}
+y &= \frac{ f(x)f(y)}{xf(f(f(y)/x)/y)} \\
+x &= \frac{y f( xf(f(f(y)/x)/y)/f(y)}{f(f(y)/x)}.
+\end{align*}
+This gives us 
+\begin{align*}
+ \frac{f(x)}{y} &= \frac{ xf(f(f(y)/x)/y)}{f(y)} \\
+xf\left(\frac{f(y)}{x}\right) &= y f\left( \frac{ xf(f(f(y)/x)/y)}{f(y)}\right).
+\end{align*}
+We note that the right hand side of the first equation can be plugged into the right hand side of the second equation to give us 
+\begin{equation}
+\label{period5relation}
+xf\left(\frac{f(y)}{x}\right) = y f\left(\frac{f(x)}{y}\right).
+\end{equation}
+Now if $f$ is some polynomial it takes the form $f(z) = b_n z^n + \cdots + b_1 z + b_0$, with $b_n \neq 0$. Plugging this definition into Equation \ref{period5relation} gives us 
+\begin{align*}
+&x\left( b_n \left( \frac{f(y)}{x}\right)^n + \cdots + b_1 \left( \frac{f(y)}{x}\right) + b_0 \right) = \\
+& y\left( b_n \left( \frac{f(x)}{y}\right)^n + \cdots + b_1 \left( \frac{f(x)}{y}\right) + b_0 \right). 
+\end{align*}
+Since $x$ and $y$ can take any values, we can set $x=1$ and let $y$ be arbitrary.
+The largest exponent of $y$ on the left hand side is $n^n$ while the largest exponent of $y$ on the right hand side is $1$.
+Since $y$ we can make it arbitrarily large so that the term with the largest exponent dominates, this gives us that $n^n=1$ so $n=1$ and $f(z) =b_1 z + b_0$.
+Plugging this back into Equation \ref{period5relation} gives us
+\begin{equation*}
+x\left(b_1 \left( \frac{b_1 y + b_0}{x} \right) + b_0 \right) = y\left(b_1 \left( \frac{b_1 x + b_0}{y} \right) + b_0 \right),
+\end{equation*}
+which simplifies to 
+\begin{equation*}
+b_1^2 y + b_0 x = b_1^2 x + b_0 y.
+\end{equation*}
+Setting $x=0$ we must have $b_0=b_1^2$. Therefore in order for the recurrence relation to have period 5 we must have $f(z)=cy+c^2$, as desired. 
 \end{proof}

### 2014-11-25 draft.tex
Added period 2 non result
Also some small edits throughout

@@
 \section{The case of $F(x,y) = f(y)/x$}
-\emph{Written by Erik Waingarten, edited by Perry Kleinhenz and Fermi Ma}
+\emph{Written by Erik Waingarten and Perry Kleinhenz, edited by Fermi Ma}
 
@@
 F(x,y) = \dfrac{f(y)}{x}
-\end{equation}. In other words, the sequences are defined by the relation
+\end{equation}. 
+In other words, the sequences are defined by the relation
 \begin{equation*}
@@
 \end{equation*}
-In the introduction, we've already seen two functions of this form that are periodic. Namely, $f(y) = 1$ and $f(y) = \frac{1}{y}$.
+In the introduction, we've already seen two functions of this form that are periodic. Namely, $$f(y) = 1,$$ and $$f(y) = \frac{1}{y}.$$
+
+At first glance it is unclear if using functions of this form we can produce a recurrence relation for an arbitrary period.
+It is also unclear if all functions of a particular period will take the same form.
+In this section we classify functions of the form of equation \ref{eq:firstcase} for period 2,3,4 and 5.
+
+\begin{proposition} 
+There are no $F$ of the form in equation \ref{eq:firstcase} with period 2.
+\end{proposition}
+\begin{proof}
+Assume otherwise so there is some $f$ of one variable that produces a recurrence relation of period 2. Then we must have 
+\begin{equation*}
+x = \frac{f(y)}{x},
+\end{equation*}
+or 
+\begin{equation*}
+x^2 = f(y).
+\end{equation*}
+Since this must hold for arbitrary $x$ and $y$, we can set $x=0$ and find that $f(y)=0$ for all $y$.
+But if we set $x=1$ we find that $f(y)=1$ for all $y$.
+This is a contradiction and so no such $f$ can exist.
+\end{proof}
 
@@
 \section{Rational/Linear F}
+\emph{Written by Perry Kleinhenz, edited by Fermi Ma and Erik Waingarten}
 In this section we consider an $F$ which is a rational function composed of arbitrary linear functions. That is 
@@
 \end{proof}
-
 \end{document}

### 2014-11-26 draft.tex
Added period 6 to section 2

@@
 
+We can also perform this analysis for period $6$  
+\begin{proposition}
+If $F$ is of the form in equation ~\ref{eq:firstcase} and has period 6 and $f$ is a polynomial then $f(y) = cy$. 
+\end{proposition}
+\begin{proof} 
+It is simple to see that $f(y)=cy$ produces a recurrence of period 6.
+Now we would like to show that all polynomial $f$ must be of this form.
+If we consider some arbitrary $f$ we know that we must have
+\begin{align*}
+a_6 =x = \frac{f(a_5)}{a_4} \\ 
+a_7 = y = \frac{f(a_6)}{a_5},
+\end{align*}
+and so $a_5 = \frac{f(x)}{y}$. This also gives us that 
+\begin{equation*}
+a_4 x = f\left( \frac{f(x)}{y} \right).
+\end{equation*}
+Noting that 
+\begin{equation*}
+a_4 = \frac{ x f(f(f(y)/x)/y)}{f(y)}, 
+\end{equation*}
+we obtain 
+\begin{equation}
+\label{period6}
+ f\left( \frac{f(x)}{y} \right) = \frac{ x^2 f(f(f(y)/x)/y)}{f(y)}.
+\end{equation}
+Since $x$ and $y$ can take any values, we can set $y=1$ and let $x$ be arbitrary.
+Furthermore since $f$ is some polynomial it takes the form $f(z) = b_n z^n + \cdots + b_1 z +b_0$.
+Plugging these two into Equation \ref{period6} gives us
+\begin{equation*}
+f(b_n x^n + \cdots + b_1 x + b_0) = x^2 f\left( b_n \frac{f(1)^n}{x^n} + \cdots + b_1 \frac{f(1)}{x} + b_0 \right).
+\end{equation*}
+We note that the largest exponent of $x$ on the left hand side is $n^n$ while the largest exponent of $y$ on the right hand side is $x^2$ if $b_0 \neq 0$.
+Since we can make $x$ arbitrarily large so that the term with the largest exponent dominates, this gives us that we must have $n^n=2$ if $b \neq 0$.
+This equation has no integer solutions and so we must have $b_0 =0$.
+Now if $b_1 \neq 0$ the largest exponent on the right hand side is $1$ and $n^n=1$ is solved by $n=1$ and so $f(z) = b_1 z$ as desired.
+\end{proof}
+
 \section{Rational/Linear F}

### 2014-11-26 draft.tex
Generating Function added

@@
 
+\subsection{Generating Function for $\alpha_k$}
+If we have the recurrence relation for $\alpha_k$ 
+\begin{equation*}
+\alpha_k = n \alpha_{k-1} - \alpha_{k-2}, 
+\end{equation*}
+we can use generating functions to find a closed form for $\alpha$. If we let $G(\xi)$ be the generating function of $\alpha_k$, that is 
+\begin{equation*}
+G(\xi) = \sum_{k=0}^{\infty} a_k \xi^k,
+\end{equation*}
+then using the above recurrence relation we know that 
+\begin{equation*}
+G(\xi) -\alpha_0 - \alpha_1 \xi = n \xi G(\xi) - \alpha_0 \xi - \xi^2 G(\xi).
+\end{equation*}
+W e can see that this holds as 
+\begin{align*}
+G(\xi) &= \alpha_0 + &\alpha_1 \xi + &\alpha_2 \xi^2 + \cdots \\
+n \xi G(\xi) &= &n\alpha_0 \xi + &n\alpha_1 \xi^2 + n\alpha_2 \xi^3 + \cdots \\
+\xi^2 G(\xi) &= &&\alpha_0 \xi^2 + \alpha_1 \xi^3 + \alpha_2 \xi^4 + \cdots.
+\end{align*}
+Therefore we can see 
+\begin{equation*}
+G( \xi) (1-n \xi + \xi^2) = n\alpha_0 + \alpha_1 \xi - n\alpha_0 \xi,
+\end{equation*}
+and so simplifying and using the fact that $\alpha_0=1, \alpha_1=0$ gives us 
+\begin{equation*}
+G(\xi) = \frac{ 1 - n\xi}{1 - n \xi + \xi^2} .
+\end{equation*}
+Now we recall that our goal is to establish what $n$ we must choose in order for our sequence to be periodic of period $p$.
+In order for this to occur we must have $\alpha_p= \alpha_0$ and $\alpha_{p+1} = \alpha_1$.
+This gives us that
+\begin{align*}
+G(\xi) = &\alpha_0 + \alpha_1 \xi + \alpha_2 \xi^2 + \cdots + \alpha_{p-1} \xi^{p-1} \\
++ \alpha_p(&\alpha_0 + \alpha_1 \xi + \alpha_2 \xi^2 + \cdots + \alpha_{p-1} \xi^{p-1}) \\ 
++ \cdots 
+\end{align*}
+and so 
+\begin{equation*}
+G(\xi) = \frac{1}{1- \xi^p} (\alpha_0 + \alpha_1 \xi + \alpha_2 \xi^2 + \cdots + \alpha_{p-1} \xi^{p-1}).
+\end{equation*}
+Combining these two relations gives us that if our sequence is of period $p$ then 
+\begin{equation*}
+\frac{ 1 - n\xi}{1 - n \xi + \xi^2} = \frac{1}{1- \xi^p} (\alpha_0 + \alpha_1 \xi + \alpha_2 \xi^2 + \cdots + \alpha_{p-1} \xi^{p-1}).
+\end{equation*}
+
+We also know that since the $\alpha_k$ are the coefficients of the power series of $G(\xi)$ we know that 
+\begin{equation*}
+\alpha_k = \frac{1}{k!} \frac{d^k}{d \xi^k} G(\xi) |_{\xi=0}.
+\end{equation*}
+
 \section{Rational/Linear F}

### 2014-11-27 draft.tex
Edited Intro

@@
 \section{Introduction}
-\emph{Written by Erik Waingarten}
+\emph{Written by Erik Waingarten and Perry Kleinhenz, edited by Fermi Ma}
 
-In this paper, we will study recurrences with \textit{memory two}.
-By memory two, we mean that the sequence can be described by a recurrence where a certain number depends on the previous two numbers.
-We can define a sequence $a_0, a_1, a_2, \dots$ recursively using a function $F(x,y)$ of two variables, where we assign
-\[ a_{n+1} = F(a_n, a_{n-1}) \]
-Note that this is the ultimate generalization of recurrences which depends on the previous two terms.
-The famous Fibonacci sequence fits this mold: we can let $F(x,y) = x + y$, and the recurrence will yield
-\[ a_{n+1} = a_n + a_{n-1} \]
-If we let $a_0 = a_1 = 1$, we get the Fibonacci sequence.
-In this paper, we will focus on the properties that arise out of different definitions of the functions $F(x,y)$, independent of the intial terms.
-So usually, we will let $a_0 = x$ and $a_1 = y$, and we assume that $x$ and $y$ can take on any values.
-We will say that a recursive definition is \textit{periodic} if, with indeterminate intiail values $a_0 = x$ and $a_1 = y$, there is an integer $n>0$ such that $a_n = x$ and $a_{n+1} = y$.
-The \emph{period} is the smallest such $n$.
+In this paper, we study recurrent sequences in which a the value of a term is defined as a function of the previous two terms.
+That is we consider sequences $a_0, a_1, a_2, \dots$ defined recursively using a function $F(x,y)$ of two variables, where we set
+\begin{equation*}
+a_{n+1} = F(a_n, a_{n-1}).
+\end{equation*}
+It is clear that any recurrence which depends on the previous two terms can be expressed in this form. For example the famous Fibonacci sequence fits this mold: if we define $F(x,y) = x + y$, then 
+\begin{equation*}
+a_{n+1} = a_n + a_{n-1},
+\end{equation*}
+and letting $a_0 =0 , a_1 = 1$, produces the Fibonacci sequence.
 
-We can compute some simple examples to promote our search. 
-\begin{itemize}
-\item $F(x,y) = y$: $x, y, x, y, x, \dots$, so we get period $2$.
-\item $F(x,y) = \dfrac{1}{xy}$: $x, y, \dfrac{1}{xy}, x, y, \dots$, so we get period $3$.
-\item $F(x,y) = \dfrac{1}{x}$: $x, y, \dfrac{1}{x}, \dfrac{1}{y}, x, y, \dots$, so we get period $4$.
-\end{itemize}
+In this paper we focus on whether or not a function $F$ will produce a sequence which is \emph{periodic} for any values of $a_0$ and $a_1$.
+In order to make this notion precise we give a formal definition.
+\begin{definition}
+A recurrence relation $F(x,y)$ is \textit{periodic} if  there exists an integer $n>0$ such that for any $x,y$, when $a_0 = x$ and $a_1 = y$ we have $a_n = x$ and $a_{n+1} = y$.
+The \emph{period} of $F$ is the smallest such $n$.
+\end{definition}
 
-There are some functions $F(x,y)$ such as the one generating the Fibonacci sequence which do not yield periodic sequences.
-One can ask, is there a simple test that determines whether a function yields a periodic sequence?
-Can we characterize the such functions?
-What are the possible periods?
+%We can compute some simple examples to promote our search. 
+%\begin{itemize}
+%\item $F(x,y) = y$: $x, y, x, y, x, \dots$, so we get period $2$.
+%\item $F(x,y) = \dfrac{1}{xy}$: $x, y, \dfrac{1}{xy}, x, y, \dots$, so we get period $3$.
+%\item $F(x,y) = \dfrac{1}{x}$: $x, y, \dfrac{1}{x}, \dfrac{1}{y}, x, y, \dots$, so we get period $4$.
+%\end{itemize}
 
-These are questions that we hope to answer.
+In Section 2 we explore a simplification of the question; we only consider $F$ of the form $F(x,y)=f(y)/x$.
+If we assume that $f$ is a polynomial we can completely classify such $F$ of period 2,3,4,5 and 6.
+We also show that for any $n>0$ we can produce a $f(y)$ such that $F$ has period $n$.
+In Section 3 we look at another simplification of the question; we consider $F$ of the form $f(x,y)/g(x,y)$ where $f$ and $g$ are linear polynomials.
+We are able to completely describe $F$ of period 2 and 3.
 

### 2014-11-27 draft.tex
added last section

@@
 \newtheorem{proposition}{Proposition}
+\newtheorem{definition}{Definition}
 
@@
 If we assume that $f$ is a polynomial we can completely classify such $F$ of period 2,3,4,5 and 6.
-We also show that for any $n>0$ we can produce a $f(y)$ such that $F$ has period $n$.
 In Section 3 we look at another simplification of the question; we consider $F$ of the form $f(x,y)/g(x,y)$ where $f$ and $g$ are linear polynomials.
 We are able to completely describe $F$ of period 2 and 3.
+In the final section, we show a method that given any period, (we conjecture) will produce a function of the form $F(x,y) = y^n/x$ which attains that period.
+For this last part, we do not assume that $n$ is an integer.
 
@@
 
-\subsection{Generating Function for $\alpha_k$}
-If we have the recurrence relation for $\alpha_k$ 
-\begin{equation*}
-\alpha_k = n \alpha_{k-1} - \alpha_{k-2}, 
-\end{equation*}
-we can use generating functions to find a closed form for $\alpha$. If we let $G(\xi)$ be the generating function of $\alpha_k$, that is 
-\begin{equation*}
-G(\xi) = \sum_{k=0}^{\infty} a_k \xi^k,
-\end{equation*}
-then using the above recurrence relation we know that 
-\begin{equation*}
-G(\xi) -\alpha_0 - \alpha_1 \xi = n \xi G(\xi) - \alpha_0 \xi - \xi^2 G(\xi).
-\end{equation*}
-W e can see that this holds as 
-\begin{align*}
-G(\xi) &= \alpha_0 + &\alpha_1 \xi + &\alpha_2 \xi^2 + \cdots \\
-n \xi G(\xi) &= &n\alpha_0 \xi + &n\alpha_1 \xi^2 + n\alpha_2 \xi^3 + \cdots \\
-\xi^2 G(\xi) &= &&\alpha_0 \xi^2 + \alpha_1 \xi^3 + \alpha_2 \xi^4 + \cdots.
-\end{align*}
-Therefore we can see 
-\begin{equation*}
-G( \xi) (1-n \xi + \xi^2) = n\alpha_0 + \alpha_1 \xi - n\alpha_0 \xi,
-\end{equation*}
-and so simplifying and using the fact that $\alpha_0=1, \alpha_1=0$ gives us 
-\begin{equation*}
-G(\xi) = \frac{ 1 - n\xi}{1 - n \xi + \xi^2} .
-\end{equation*}
-Now we recall that our goal is to establish what $n$ we must choose in order for our sequence to be periodic of period $p$.
-In order for this to occur we must have $\alpha_p= \alpha_0$ and $\alpha_{p+1} = \alpha_1$.
-This gives us that
-\begin{align*}
-G(\xi) = &\alpha_0 + \alpha_1 \xi + \alpha_2 \xi^2 + \cdots + \alpha_{p-1} \xi^{p-1} \\
-+ \alpha_p(&\alpha_0 + \alpha_1 \xi + \alpha_2 \xi^2 + \cdots + \alpha_{p-1} \xi^{p-1}) \\ 
-+ \cdots 
-\end{align*}
-and so 
-\begin{equation*}
-G(\xi) = \frac{1}{1- \xi^p} (\alpha_0 + \alpha_1 \xi + \alpha_2 \xi^2 + \cdots + \alpha_{p-1} \xi^{p-1}).
-\end{equation*}
-Combining these two relations gives us that if our sequence is of period $p$ then 
-\begin{equation*}
-\frac{ 1 - n\xi}{1 - n \xi + \xi^2} = \frac{1}{1- \xi^p} (\alpha_0 + \alpha_1 \xi + \alpha_2 \xi^2 + \cdots + \alpha_{p-1} \xi^{p-1}).
-\end{equation*}
-
-We also know that since the $\alpha_k$ are the coefficients of the power series of $G(\xi)$ we know that 
-\begin{equation*}
-\alpha_k = \frac{1}{k!} \frac{d^k}{d \xi^k} G(\xi) |_{\xi=0}.
-\end{equation*}
-
 \section{Rational/Linear F}
@@
 \end{proof}
+
+\section{The $f(y) = y^n$ Case}
+
+\emph{Written by Fermi Ma and Perry Kleinhenz, edited by Erik Waingarten}\\
+
+Consider the case where $F(x,y) = f(y)/x$ where $f(y) = y^n$. Then the sequence can be written as follows
+\[ x^1y^0, x^0y^1, x^{-1}y^{n}, x^{-n}y^{n^2-1}, x^{-n^2+1}y^{n^3-2n},x^{-n^3+n^2+n}y^{n^4-3n^2+1}, \dots \]
+
+The interesting thing to note is that all of the terms in the sequence are now monomials.
+This makes the analysis much easier.
+Now let $\alpha_k$ be the sequence of the exponents of $x$ in the above sequence, and let $\beta_k$ be the sequence of exponents of $y$.
+So we have
+\begin{align*}
+\alpha_0 &= 1  &\beta_0& = 0\\
+\alpha_1 &= 0 &\beta_1& = 1\\
+\alpha_2 &= -1  &\beta_2& = n\\
+\alpha_3 &= -n &\beta_3& = n^2-1\\
+\alpha_4 &= -n^2+1 &\beta_4& = n^3-2n\\
+\alpha_5 &= -n^3+2n &\beta_5& =n^4-3n^2+1\\ 
+\alpha_6 &= -n^4+3n^2 -1 &\beta_6& =n^5-4n^3+3n \\ 
+\alpha_7 &= -n^5+4n^3 - 3n &\beta_7& =n^6-5n^4+6n^2 - 1
+\end{align*}
+
+We can use these $\{\alpha_i\}$ and $\{\beta_i\}$ sequences to get values of $n$ that achieve certain periods.
+For example, if we want a function of the form $F(x,y) = y^n/x$ with period 5, we simply set $\alpha_5 = \alpha_0 = 1$, $\beta_5 = \beta_0 = 0$, $\alpha_6 = \alpha_1 = 0$, and $\beta_6 = \beta_1 = 1$.
+This gives us a system of four equations in one variable
+\begin{align*}
+-n^3+2n &= 1\\
+n^4-3n^2+1&=0\\
+-n^4+3n^2 -1&= 0\\
+n^5-4n^3+3&n=1\\
+\end{align*}
+There is no guarantee that this system has a solution, but it turns out that setting $n = -\frac{1+\sqrt{5}}{2} = \phi$, the golden ratio, works.
+This tells us that $F(x,y) = y^{-\phi}/x$ is periodic with period 5, and we can indeed check that this is the case.
+
+In our numerical calculations, it seems like this system of equations always \emph{does} has a real solution, which leads us to conjecture that for any period strictly greater than 2, there is a function of the form $y^n/x$ with that period.
+
+\subsection{Properties of $\alpha_k$ and $\beta_k$}
+
+We first notice that $\alpha_k$ and $\beta_k$ are similar sequences, as they can be defined as
+\begin{align*}
+\alpha_0 = 1, \alpha_1 = 0, \alpha_k = n\alpha_{k-1} - \alpha_{k-2}\\
+\beta_0 = 0, \beta_1 = 1, \beta_k = n\beta_{k-1} - \beta_{k-2}
+\end{align*}
+
+The recurrence relation follows from simply inspecting the function $F(x,y) = y^n/x$.
+
+Note also that $-\beta_k = \alpha_{k+1}$.
+This follows from the fact that this holds true from looking at the $k =0$ and $k = 1$ cases, and then noticing that the recurrence relations preserve this property.
+
+We also note that $\beta_k$ can be written as 
+\begin{align*}
+\binom{k-1}{k-1} n^{k-1} - \binom{k-2}{k-3}n^{k-3} +\binom{k-3}{k-5}n^{k-5} -\binom{k-3}{k-7}n^{k-7} + \dots \\
+=\sum_{i = 0}^{\lfloor (k-1)/2 \rfloor} (-1)^i\binom{k-1-i}{k-1-2i}n^{k-1-2i}\\
+\end{align*}
+for $k \geq 1$.
+
+To check this, note that it holds for $k = 1$ and $k = 2$, and then plug it in to the recurrence relation
+\begin{align*}
+\beta_k =& n\beta_{k-1} - \beta_{k-2}\\
+\sum_{i = 0}^{\lfloor (k-1)/2 \rfloor} (-1)^i\binom{k-1-i}{k-1-2i}n^{k-1-2i} = & n \sum_{i = 0}^{\lfloor (k-2)/2 \rfloor} (-1)^i\binom{k-2-i}{k-2-2i}n^{k-2-2i} \\
+& +\sum_{i = 0}^{\lfloor (k-3)/2 \rfloor} (-1)^i\binom{k-3-i}{k-3-2i}n^{k-3-2i}\\
+\end{align*}
+Checking this equation for when $k$ is even and when $k$ is odd, as well as using combinatorial identities, shows that this is true.
+
+So we have an expression for $\beta_k$, and this in turn gives us an expression for $\alpha_k$ as noted above.
+Thus, we know that if we want to attain a specific period $p$, we have to solve equations involving these known expressions.
+
+It remains to show that these equations always produce a real solution for $n$.
+
+\subsection{Generating Function for $\alpha_k$}
+If we have the recurrence relation for $\alpha_k$ 
+\begin{equation*}
+\alpha_k = n \alpha_{k-1} - \alpha_{k-2}, 
+\end{equation*}
+we can use generating functions to find a closed form for $\alpha$. If we let $G(\xi)$ be the generating function of $\alpha_k$, that is 
+\begin{equation*}
+G(\xi) = \sum_{k=0}^{\infty} a_k \xi^k,
+\end{equation*}
+then using the above recurrence relation we know that 
+\begin{equation*}
+G(\xi) -\alpha_0 - \alpha_1 \xi = n \xi G(\xi) - \alpha_0 \xi - \xi^2 G(\xi).
+\end{equation*}
+W e can see that this holds as 
+\begin{align*}
+G(\xi) &= \alpha_0 + &\alpha_1 \xi + &\alpha_2 \xi^2 + \cdots \\
+n \xi G(\xi) &= &n\alpha_0 \xi + &n\alpha_1 \xi^2 + n\alpha_2 \xi^3 + \cdots \\
+\xi^2 G(\xi) &= &&\alpha_0 \xi^2 + \alpha_1 \xi^3 + \alpha_2 \xi^4 + \cdots.
+\end{align*}
+Therefore we can see 
+\begin{equation*}
+G( \xi) (1-n \xi + \xi^2) = n\alpha_0 + \alpha_1 \xi - n\alpha_0 \xi,
+\end{equation*}
+and so simplifying and using the fact that $\alpha_0=1, \alpha_1=0$ gives us 
+\begin{equation*}
+G(\xi) = \frac{ 1 - n\xi}{1 - n \xi + \xi^2} .
+\end{equation*}
+Now we recall that our goal is to establish what $n$ we must choose in order for our sequence to be periodic of period $p$.
+In order for this to occur we must have $\alpha_p= \alpha_0$ and $\alpha_{p+1} = \alpha_1$.
+This gives us that
+\begin{align*}
+G(\xi) = &\alpha_0 + \alpha_1 \xi + \alpha_2 \xi^2 + \cdots + \alpha_{p-1} \xi^{p-1} \\
++ \alpha_p(&\alpha_0 + \alpha_1 \xi + \alpha_2 \xi^2 + \cdots + \alpha_{p-1} \xi^{p-1}) \\ 
++ \cdots 
+\end{align*}
+and so 
+\begin{equation*}
+G(\xi) = \frac{1}{1- \xi^p} (\alpha_0 + \alpha_1 \xi + \alpha_2 \xi^2 + \cdots + \alpha_{p-1} \xi^{p-1}).
+\end{equation*}
+Combining these two relations gives us that if our sequence is of period $p$ then 
+\begin{equation*}
+\frac{ 1 - n\xi}{1 - n \xi + \xi^2} = \frac{1}{1- \xi^p} (\alpha_0 + \alpha_1 \xi + \alpha_2 \xi^2 + \cdots + \alpha_{p-1} \xi^{p-1}).
+\end{equation*}
+
+We also know that since the $\alpha_k$ are the coefficients of the power series of $G(\xi)$ we know that 
+\begin{equation*}
+\alpha_k = \frac{1}{k!} \frac{d^k}{d \xi^k} G(\xi) |_{\xi=0}.
+\end{equation*}
+
 \end{document}

### 2014-12-05 draft.tex
Added subsection on Existence of Common Solutions

@@
 
+\subsection{Existence of Common Solutions}
+
+\begin{lemma} 
+\label{ab} For $k\geq 1$
+\begin{equation*}
+\alpha_{k+1} = - \beta_{k}.
+\end{equation*}
+\end{lemma}
+\begin{proof}
+We will show this using induction.
+As a base case note that $\alpha_2 = -1 = \beta_1$, and $\alpha_3 = -n = \beta_2$.
+Now if we assume this holds for $k \leq m$ and would like to show it holds for $k = m+1$ consider $\alpha_{m+1}$
+\begin{equation*}
+\alpha_{m+1} = n \alpha_{m} - \alpha_{m-1}.
+\end{equation*}
+Well $\alpha_m = -\beta_{m-1}$ and $\alpha_{m-1} = - \beta_{m-2}$ and so 
+\begin{equation*}
+\alpha_{m+1} = - n \beta_{m-1} + \beta_{m-2} = -\beta_{m},
+\end{equation*}
+as desired.
+\end{proof}
+Now if we want to choose an $n$ such that  $F(x,y)$ has period $p$, our choice of $n$ must solve the equations 
+\begin{align*}
+x^{\alpha_p} y^{\beta_p} = x^{1}y^{0} \\
+x^{\alpha_{p+1}} y^{\beta_{p+1}} = x^{0}y^{1}.
+\end{align*}
+Or in other terms
+\begin{align*}
+\alpha_p &=1 \\
+\beta_p &=0\\ 
+\alpha_{p+1} &= 0 \\
+\beta_{p+1} &= 1.
+\end{align*}
+However as shown in Lemma \ref{ab} above $\alpha_{p+1} = -\beta_p$, and so $\beta_p=0$ and $\alpha_{p+1} =0$ are the same equation.  We also know by the recurrence relation for $\beta$ that 
+\begin{equation*}
+\beta_{p+1} = n \beta_{p} - \beta_{p-1}.
+\end{equation*}
+Substituting $\alpha_p = -\beta_{p-1}$ and $\beta_{p}=0$ gives us 
+\begin{equation*}
+\beta_{p+1} = \alpha_p.
+\end{equation*} 
+Therefore we actually only need to find a value for $n$ which satisfies the two equations
+\begin{align*}
+\alpha_p &=1\\
+\alpha_{p+1}&=0.
+\end{align*}
+
 \subsection{Generating Function for $\alpha_k$}

### 2014-12-05 draft.tex
Moved lemma to better spot

@@
 
-Note also that $-\beta_k = \alpha_{k+1}$.
-This follows from the fact that this holds true from looking at the $k =0$ and $k = 1$ cases, and then noticing that the recurrence relations preserve this property.
+We also have a relation between $\alpha_k$ and $\beta_k$. 
+\begin{lemma} 
+\label{ab} For $k\geq 0$
+\begin{equation*}
+\alpha_{k+1} = - \beta_{k}.
+\end{equation*}
+\end{lemma}
+\begin{proof}
+We will show this using induction.
+As a base case note that $\alpha_1 = 0 = \beta_0$, and $\alpha_2 = -n = \beta_1$.
+Now if we assume this holds for $k \leq m$ and would like to show it holds for $k = m+1$ consider $\alpha_{m+1}$
+\begin{equation*}
+\alpha_{m+1} = n \alpha_{m} - \alpha_{m-1}.
+\end{equation*}
+Well $\alpha_m = -\beta_{m-1}$ and $\alpha_{m-1} = - \beta_{m-2}$ and so 
+\begin{equation*}
+\alpha_{m+1} = - n \beta_{m-1} + \beta_{m-2} = -\beta_{m},
+\end{equation*}
+as desired.
+\end{proof}
 
@@
 
-\begin{lemma} 
-\label{ab} For $k\geq 1$
-\begin{equation*}
-\alpha_{k+1} = - \beta_{k}.
-\end{equation*}
-\end{lemma}
-\begin{proof}
-We will show this using induction.
-As a base case note that $\alpha_2 = -1 = \beta_1$, and $\alpha_3 = -n = \beta_2$.
-Now if we assume this holds for $k \leq m$ and would like to show it holds for $k = m+1$ consider $\alpha_{m+1}$
-\begin{equation*}
-\alpha_{m+1} = n \alpha_{m} - \alpha_{m-1}.
-\end{equation*}
-Well $\alpha_m = -\beta_{m-1}$ and $\alpha_{m-1} = - \beta_{m-2}$ and so 
-\begin{equation*}
-\alpha_{m+1} = - n \beta_{m-1} + \beta_{m-2} = -\beta_{m},
-\end{equation*}
-as desired.
-\end{proof}
 Now if we want to choose an $n$ such that  $F(x,y)$ has period $p$, our choice of $n$ must solve the equations 

### 2014-12-07 draft.tex
Added Gen Function Result

@@
 \end{equation*}
+We can deduce additional properties of $n$ from this relation. Note that in order to have equality of rational functions, the zeroes of the functions on both sides must be the same. 
+The only zero on the left hand side is $\xi = 1/n$, (note that $1-n*1/n + 1/n^2 \neq 0$).
+The numerator of the left hand side has $p-1$ zeroes in the complex plane, while the denominator has exactly $p$ zeroes.
+In fact we know that the zeroes of $1 - \xi^p$ are $\xi = e^{2 \pi i k/p}$ for $k=0,1,2, \ldots, p-1$.
+Therefore $p-2$ of the zeroes of the numerator polynomial must be $p$th roots of unity, while the last root must be $\xi = 1/n$.
 
-We also know that since the $\alpha_k$ are the coefficients of the power series of $G(\xi)$ we know that 
+Note also that the locations of discontinuities for both functions must be the same.
+Therefore we must have that the zeroes of $1-n\xi + \xi^2$ are the same as those zeroes of the denominator of the left hand side which were not canceled out.
+Thus for some $l$ and $m$, we must have
+\begin{align*}
+(\xi - e^{2 \pi i l/p})(\xi - e^{2 \pi i m/p}) = 1 - n \xi + \xi^2,
+\end{align*}
+or 
+\begin{align*}
+n = e^{2 \pi i l/p} + e^{2 \pi i m/p} \\
+1 = e^{2 \pi i (l+m)/p}.
+\end{align*}
+So $n$ must be the sum of some $p$th roots of unity, and in fact these roots of unity must be conjugates of one another, so $n$ is always real and 
+\begin{equation*}
+n= 2 \cos(2 \pi l/p), 
+\end{equation*}
+for some $l \in \{0, 1,2, \ldots, p-1\}$. 
+Since the $\alpha_k$ are the coefficients of the power series of $G(\xi)$ we also know that 
 \begin{equation*}

### 2014-12-08 draft.tex
finished introduction

--- 2014-12-05 draft.tex
@@
 \newtheorem{definition}{Definition}
+\newtheorem{lemma}{Lemma}
 
@@
 \section{Introduction}
-\emph{Written by Erik Waingarten and Perry Kleinhenz, edited by Fermi Ma}
+\emph{Written by Erik Waingarten, Perry Kleinhenz, and Fermi Ma}
 
-In this paper, we study recurrent sequences in which a the value of a term is defined as a function of the previous two terms.
-That is we consider sequences $a_0, a_1, a_2, \dots$ defined recursively using a function $F(x,y)$ of two variables, where we set
+In this paper, we look at sequences of the form $a_0, a_1, a_2, \dots$ defined recursively using a function $F(x,y)$ of two variables, where we set
 \begin{equation*}
@@
 \end{equation*}
-It is clear that any recurrence which depends on the previous two terms can be expressed in this form. For example the famous Fibonacci sequence fits this mold: if we define $F(x,y) = x + y$, then 
+It is clear that any recurrent sequence where the relation only depends on the previous two terms can be expressed in this form.
+For example, the famous Fibonacci sequence fits this mold: if we define $F(x,y) = x + y$, then
 \begin{equation*}
@@
 
-In this paper we focus on whether or not a function $F$ will produce a sequence which is \emph{periodic} for any values of $a_0$ and $a_1$.
+In this paper we investigate the question of whether or not a function $F$ will produce a sequence which is \emph{periodic} for all values of $a_0$ and $a_1$.
 In order to make this notion precise we give a formal definition.
 \begin{definition}
-A recurrence relation $F(x,y)$ is \textit{periodic} if  there exists an integer $n>0$ such that for any $x,y$, when $a_0 = x$ and $a_1 = y$ we have $a_n = x$ and $a_{n+1} = y$.
-The \emph{period} of $F$ is the smallest such $n$.
+A recurrence relation $F(x,y)$ is \textit{periodic} if there exists an integer $p>0$ such that for any $x,y$, when $a_0 = x$ and $a_1 = y$ we have $a_p = x$ and $a_{p+1} = y$.
+In this paper, the period $p$ will refer to the smallest such integer.
 \end{definition}
 
-%We can compute some simple examples to promote our search. 
-%\begin{itemize}
-%\item $F(x,y) = y$: $x, y, x, y, x, \dots$, so we get period $2$.
-%\item $F(x,y) = \dfrac{1}{xy}$: $x, y, \dfrac{1}{xy}, x, y, \dots$, so we get period $3$.
-%\item $F(x,y) = \dfrac{1}{x}$: $x, y, \dfrac{1}{x}, \dfrac{1}{y}, x, y, \dots$, so we get period $4$.
-%\end{itemize}
-
-In Section 2 we explore a simplification of the question; we only consider $F$ of the form $F(x,y)=f(y)/x$.
-If we assume that $f$ is a polynomial we can completely classify such $F$ of period 2,3,4,5 and 6.
-In Section 3 we look at another simplification of the question; we consider $F$ of the form $f(x,y)/g(x,y)$ where $f$ and $g$ are linear polynomials.
-We are able to completely describe $F$ of period 2 and 3.
-In the final section, we show a method that given any period, (we conjecture) will produce a function of the form $F(x,y) = y^n/x$ which attains that period.
-For this last part, we do not assume that $n$ is an integer.
+The paper is organized as follows.
+In Section~\ref{f(y)/x case}, we consider sequences of the form $F(x,y) = f(y)/x$ where $f(y)$ is a polynomial in $y$.
+For periods 2, 3, 4, 5, and 6, we give functions of this form that produce these periods, and show that no other functions of this form work.
+In Section~\ref{rational and linear F}, we look at another simplification of the question; we consider $F(x,y)$ of the form $f(x,y)/g(x,y)$ where $f$ and $g$ are both linear functions of $x$ and $y$.
+We are able to completely describe the functions $F(x,y)$ of this form that produce periods 2 and 3.
+Lastly, in Section~\ref{general case}, we consider the general problem of producing a periodic function $F(x,y)$ for any given period $p \geq 2$.
+We do this by looking at functions of the form $F(x,y) = y^n/x$ where $n$ can be any real or complex number.
+We give a method that we conjecture works for any given $p$, and we provide some ideas one might use to prove this conjecture.
+In addition, we support the conjecture with numerical evidence from Mathematica.
 
 \section{The case of $F(x,y) = f(y)/x$}
+\label{f(y)/x case}
 \emph{Written by Erik Waingarten and Perry Kleinhenz, edited by Fermi Ma}
@@
 \section{Rational/Linear F}
+\label{rational and linear F}
 \emph{Written by Perry Kleinhenz, edited by Fermi Ma and Erik Waingarten}
@@
 \section{The $f(y) = y^n$ Case}
+\label{general case}
 
@@
 \begin{align*}
-\binom{k-1}{k-1} n^{k-1} - \binom{k-2}{k-3}n^{k-3} +\binom{k-3}{k-5}n^{k-5} -\binom{k-3}{k-7}n^{k-7} + \dots \\
+\binom{k-1}{k-1} n^{k-1} - \binom{k-2}{k-3}n^{k-3} +\binom{k-3}{k-5}n^{k-5} -\binom{k-4}{k-7}n^{k-7} + \dots \\
 =\sum_{i = 0}^{\lfloor (k-1)/2 \rfloor} (-1)^i\binom{k-1-i}{k-1-2i}n^{k-1-2i}\\
@@
 \begin{equation*}
-G(\xi) -\alpha_0 - \alpha_1 \xi = n \xi G(\xi) - \alpha_0 \xi - \xi^2 G(\xi).
+G(\xi) -\alpha_0 - \alpha_1 \xi = n \xi G(\xi) - n \alpha_0 \xi - \xi^2 G(\xi).
 \end{equation*}

### 2014-12-08 draft.tex
finished up to the end of period 2

@@
 The paper is organized as follows.
-In Section~\ref{f(y)/x case}, we consider sequences of the form $F(x,y) = f(y)/x$ where $f(y)$ is a polynomial in $y$.
+In Section~\ref{f(y)/x case}, we consider sequences of the form $F(x,y) = f(y)/x$.
 For periods 2, 3, 4, 5, and 6, we give functions of this form that produce these periods, and show that no other functions of this form work.
@@
 
-We begin by considering the special case where
-\begin{equation}\label{eq:firstcase}
-F(x,y) = \dfrac{f(y)}{x}
-\end{equation}. 
-In other words, the sequences are defined by the relation
-\begin{equation*}
-a_{n+1} = \dfrac{f(a_{n-1})}{a_n}
-\end{equation*}
-In the introduction, we've already seen two functions of this form that are periodic. Namely, $$f(y) = 1,$$ and $$f(y) = \frac{1}{y}.$$
+We begin by investigate the special case of functions $F(x,y) = f(y)/x$.
+In this section, we look at periods 2, 3, 4, 5 and 6 as separate cases, and manage to fully classify the polynomials $f(y)$ that produce these periods.
+However, we will see in this section that our analysis increases significantly in complexity as the period increases, making it unlikely that this approach will help us deal with general periods $p$.
 
-At first glance it is unclear if using functions of this form we can produce a recurrence relation for an arbitrary period.
-It is also unclear if all functions of a particular period will take the same form.
-In this section we classify functions of the form of equation \ref{eq:firstcase} for period 2,3,4 and 5.
+\subsection{Period 2}
 
-\begin{proposition} 
-There are no $F$ of the form in equation \ref{eq:firstcase} with period 2.
-\end{proposition}
+We claim that there are no functions $f(y)/x$ that produce a period of 2. Note that for this claim, we do not need any assumptions about $f(y)$.
+
 \begin{proof}
-Assume otherwise so there is some $f$ of one variable that produces a recurrence relation of period 2. Then we must have 
+Assume otherwise. Then the sequence looks like
+\[ x,y,x,y,x,y,\dots , \]
+and in particular we have two expressions for the third term of the sequence. By definition, the third term is $f(y)/x$, but the periodicity requirement makes it equal to $x$. So we must have
 \begin{equation*}
@@
 \end{equation*}
-or 
+or equivalently
 \begin{equation*}
@@
 \end{equation*}
-Since this must hold for arbitrary $x$ and $y$, we can set $x=0$ and find that $f(y)=0$ for all $y$.
-But if we set $x=1$ we find that $f(y)=1$ for all $y$.
-This is a contradiction and so no such $f$ can exist.
+This equation must hold for arbitrary $x$ and $y$, but setting $x = 0$ gives $f(y) = 0$ for all $y$, and setting $x = 1$ gives $f(y) = 1$ for all $y$. Contradiction.
 \end{proof}
 
-\begin{proposition}
-If $F$ is of the form in equation ~\ref{eq:firstcase} and has period 3, then $F(x,y) = \dfrac{c}{xy}$.
-\end{proposition}
+\subsection{Period 3}
+
+We claim that all functions $f(y)/x$ that produce a period of 3 are of the form $f(y) = \frac{c}{y}$.
 

### 2014-12-08 draft.tex
finished up to the end of period 4

@@
 In Section~\ref{f(y)/x case}, we consider sequences of the form $F(x,y) = f(y)/x$.
-For periods 2, 3, 4, 5, and 6, we give functions of this form that produce these periods, and show that no other functions of this form work.
+For periods 2, 3, 4, 5, and 6, we give functions of this form that produce these periods, and (under certain assumptions) show that no other functions of this form work.
 In Section~\ref{rational and linear F}, we look at another simplification of the question; we consider $F(x,y)$ of the form $f(x,y)/g(x,y)$ where $f$ and $g$ are both linear functions of $x$ and $y$.
@@
 In this section, we look at periods 2, 3, 4, 5 and 6 as separate cases, and manage to fully classify the polynomials $f(y)$ that produce these periods.
+For periods 2 and 3, we do not need the assumption that we are dealing with polynomials, but we do need this assumption for periods 4, 5 and 6.
 However, we will see in this section that our analysis increases significantly in complexity as the period increases, making it unlikely that this approach will help us deal with general periods $p$.
@@
 \begin{proof}
-Assume otherwise. Then the sequence looks like
+Assume otherwise. Note the sequence looks like
 \[ x,y,x,y,x,y,\dots , \]
@@
 
-We claim that all functions $f(y)/x$ that produce a period of 3 are of the form $f(y) = \frac{c}{y}$.
+We claim that a function $f(y)/x$ if and only if it is of the form $f(y) = \frac{c}{y}$ where $c$ is some constant. We separate this claim into two propositions, which we prove separately
 
-\begin{proof}
-Consider the first 4 terms of the :
-\begin{equation*}
-x, y, \dfrac{f(y)}{x}, x, y, \dots 
-\end{equation*}
-We note that $a_4=y$ and using the recurrence relation we find that 
-\begin{equation*}
-y = \dfrac{xf(x)}{f(y)},
-\end{equation*}
-and so,
-\begin{equation*} 
-y f(y) = x f(x).
-\end{equation*}
-Now if we fix $x = 1$, we have $y f(y) = f(1)$, and so $f(y) = \dfrac{c}{y}$, where $c$ is some constant .
-\end{proof}
-
-We can do a similar analysis for period $4$.
 \begin{proposition}
-f $F$ is of the form in equation ~\ref{eq:firstcase} and has period 4 and $f$ is a polynomial then $f(y) = c$. 
+If a function of the form $f(y)/x$ produces a period 3 sequence, it must be of the form $f(y) = \frac{c}{y}$ where $c$ is some constant.
 \end{proposition}
@@
 \begin{proof}
-It is easy to check that these functions yield a sequence with period $4$, as they would form a sequence $x,y, \frac{c}{x}, \frac{c}{y}, x, y, \ldots$.
+If the period is 3, then the sequence is
+\begin{equation*}
+x, y, \dfrac{f(y)}{x}, x, y, \dfrac{f(y)}{x}, \dots
+\end{equation*}
+The fourth term of the sequence must be of the form $\frac{x f(x)}{f(y)}$, which gives the relation
+\[ y = \frac{x f(x)}{f(y)}. \]
+Recall that we defined periodicity to mean that the sequence is periodic for \emph{all} choices of $x$ and $y$. In particular, this must hold when $x = 1$, in which case the relation is
+\[ y = \frac{f(1)}{f(y)} \]
+which tells us that $f(y) = \frac{f(1)}{y}$. Since $f(1)$ is a constant, this completes the proof.
+\end{proof}
 
-Now suppose we have some non constant polynomial  $f$ that produces a sequence with period $4$. The  the first few terms of the sequence are 
+\begin{proposition}
+Any function of the form $f(y) = \frac{c}{y}$ where $c$ is a constant will produce a period 3 sequence.
+\end{proposition}
+\begin{proof}
+This follows simply by writing down the sequence.
+The third term of the sequence will be $\frac{c}{xy}$, and the fourth term must then be $\frac{cxy}{cy} = x$, and the fifth term is $\frac{cxy}{cx} = y$.
+This completes the proof, as we have cycled back to $x$ and $y$.
+ \end{proof}
+
+\subsection{Period 4}
+
+To make claims about functions $f(y)/x$ for period 4, we must assume that $f(y)$ is a polynomial in $y$. Then we get the following result.
+
+\begin{proposition}
+If $F(x,y) = f(y)/x$ and $f(y)$ is a polynomial in $y$, then the resulting sequence has period 4 if and only if $f(y) = c$ for any constant $c$
+\end{proposition}
+
+\begin{proof}
+One direction of this claim is easy to check. If we set $f(y) = c$, our sequence is
+\[x,y, \frac{c}{x}, \frac{c}{y}, x, y, \dots .\]
+
+For the harder direction, suppose we have a sequence of period 4 and that the function is $f(y)/x$. Then we know that the sequence looks like
 \begin{equation*}
@@
 \end{equation*}
-We note that $a_5 =y$ and using the recurrence relation we find that 
-\begin{equation*}
- y = \dfrac{yf(x)}{f(f(y)/x)}, 
- \end{equation*}
-simplifying gives us  
-\begin{equation*}
- f(f(y)/x) = f(x).
-\end{equation*}
-If we fix $x = 1$, we have
-\begin{equation*}
-f(f(y)) = f(1). 
-\end{equation*}
-This means that $f(f(y))$ is a constant for every $y$.
-If we let $z=f(y)$ then we can see that $f(z)-f(1)$ is a polynomial in $z$ and has infinitely many roots.
-This is a contradiction as polynomials can only have finitely many roots.
-Therefore $f$ must be a constant.
+Using the fact that the sixth term of the sequence is generated by a recurrence relation on the two previous terms, we know it must be $\dfrac{yf(x)}{f(f(y)/x)}$.
+On the other hand, periodicity tells us it is $y$, so we have
+\[ y = \dfrac{yf(x)}{f(f(y)/x)}.\]
+
+Simplifying this gives
+\[ f(f(y)/x) = f(x). \]
+
+If we set $x = 1$, then we get
+\[ f(f(y)) = f(1). \]
+
+And in particular, this tells us that $f(f(y))$ is a constant.
+Now suppose that $f(y)$ is a nonconstant polynomial.
+Then $f(y)$ can take on infinitely many values, and note that at all of these values $f(f(y)) - f(1) = 0$.
+This means that $f(f(y)) - f(1)$, a nonconstant polynomial in $f(y)$, has infinitely many roots.
+This is a contradiction, $f(y)$ must be a constant.
 \end{proof}
+
+\subsection{Period 5}
 

### 2014-12-08 draft.tex
finished period 5 and 6

@@
 
-We can also perform this analysis for period $5$  
+Similarly, for period 5, we make the assumption that $f(y)$ is a polynomial in $y$.
+
 \begin{proposition}
-If $F$ is of the form in equation ~\ref{eq:firstcase} and has period 5 and $f$ is a polynomial then $f(y) = cy+c^2$. 
+If $F(x,y) = f(y)/x$ and $f(y)$ is a polynomial in $y$, then the resulting sequence has period 5 if and only if $f(y) = cy + c^2$ for any constant $c$.
 \end{proposition}
+
 \begin{proof}
-First we must show that $a_5=a_0$ and $a_6=a_1$. Well 
+We omit the proof that this function indeed produces period 5. The proof simply involves writing out the sequence as given by the recurrence relation, and verifying that this works.
+
+We show that if the sequnce has period 5, then $f(y)$ must be of this form. We know that the sequence must look like
 \begin{equation*}
-a_2 = \frac{cy+c^2}{x},
+x,y, \frac{f(y)}{x}, \frac{f(f(y)/x)}{y}, \frac{xf( f(f(y)/x)/y)}{f(y)}, x, y, \dots .
 \end{equation*}
-and so 
+We know that the sixth term must be $\frac{y f( xf(f(f(y)/x)/y)/f(y))}{f(f(y)/x)}$ and the seventh term must be $\frac{ f(x)f(y)}{xf(f(f(y)/x)/y)}$ due to the recurrence relation.
+This gives the equations
+\begin{align*}
+x &= \frac{y f( xf(f(f(y)/x)/y)/f(y))}{f(f(y)/x)}\\
+y &= \frac{ f(x)f(y)}{xf(f(f(y)/x)/y)}.
+\end{align*}
+These equations can be rewritten as
+\begin{align*}
+xf\left(\frac{f(y)}{x}\right) &= y f\left( \frac{ xf(f(f(y)/x)/y)}{f(y)}\right) \\
+\frac{f(x)}{y} &= \frac{ xf(f(f(y)/x)/y)}{f(y)}. 
+\end{align*}
+We note that the right hand side of the second equation can be plugged into the right hand side of the first equation to give us 
 \begin{equation*}
-a_3 = \frac{ c \frac{cy+c^2}{x} +c^2}{y} = \frac{c^2y + c^3+c^3x}{xy},
+xf\left(\frac{f(y)}{x}\right) = y f\left(\frac{f(x)}{y}\right).
 \end{equation*}
-so
-\begin{equation*}
-a_4  = \frac{c \frac{cy + c^2+c^2x}{xy} +c^2}{\frac{cy+c^2}{x}} = \frac{c^2y+c^2+c^2x+c^2xy}{y(cy+c^2)} = \frac{c(c+x)}{y},
-\end{equation*}
-giving us 
-\begin{align*}
-a_5 &=\left(c \frac{c(c+x)}{y} + c^2\right) \frac{xy}{c^2y+c^3+c^3x} = \frac{c^2y+c^3+c^3x}{y} \frac{xy}{c^2y+c^3+c^3x}= x.
-\end{align*}
-We can finally calculate $a_6$ and find 
-\begin{align*}
-a_6 = (cx + c^2) \frac{y}{cx+c^2} = y
-\end{align*}
-Therefore $f(y)=cy+c^2$ is periodic with period 5 as desired.
-Now we would like to show that all polynomial $f$ must be of this form.
-So if we consider an arbitrary $f$ we know that the first few terms of the sequence will be
-\begin{equation*}
-x,y, \frac{f(y)}{x}, \frac{f(f(y)/x)}{y}, \frac{xf( f(f(y)/x)/y)}{f(y)}, x, y, \ldots
-\end{equation*}
-Now using the recurrence relation and setting $a_5=a$ and $a_6=y$, we obtain the relations
-\begin{align*}
-y &= \frac{ f(x)f(y)}{xf(f(f(y)/x)/y)} \\
-x &= \frac{y f( xf(f(f(y)/x)/y)/f(y)}{f(f(y)/x)}.
-\end{align*}
-This gives us 
-\begin{align*}
- \frac{f(x)}{y} &= \frac{ xf(f(f(y)/x)/y)}{f(y)} \\
-xf\left(\frac{f(y)}{x}\right) &= y f\left( \frac{ xf(f(f(y)/x)/y)}{f(y)}\right).
-\end{align*}
-We note that the right hand side of the first equation can be plugged into the right hand side of the second equation to give us 
-\begin{equation}
-\label{period5relation}
-xf\left(\frac{f(y)}{x}\right) = y f\left(\frac{f(x)}{y}\right).
-\end{equation}
-Now if $f$ is some polynomial it takes the form $f(z) = b_n z^n + \cdots + b_1 z + b_0$, with $b_n \neq 0$. Plugging this definition into Equation \ref{period5relation} gives us 
+Now if $f$ is some polynomial, it takes the form $f(z) = b_n z^n + \cdots + b_1 z + b_0$, with $b_n \neq 0$. Plugging this definition into the above equation gives us 
 \begin{align*}
@@
 Since $x$ and $y$ can take any values, we can set $x=1$ and let $y$ be arbitrary.
-The largest exponent of $y$ on the left hand side is $n^n$ while the largest exponent of $y$ on the right hand side is $1$.
-Since $y$ we can make it arbitrarily large so that the term with the largest exponent dominates, this gives us that $n^n=1$ so $n=1$ and $f(z) =b_1 z + b_0$.
-Plugging this back into Equation \ref{period5relation} gives us
+The largest exponent of $y$ on the left hand side is $n^2$ while the largest exponent of $y$ on the right hand side is $1$.
+Since $y$ can be arbitrarily large, the term with the largest exponent dominates.
+For large $y$, the only way the two sides can be equal is if $n^2 = 1$, and so $n = 1$.
+This means that the polynomial $f(z)$ must be linear, so we write $f(z) =b_1 z + b_0$.
+Simplifying the above equations by assuming linearity gives
 \begin{equation*}
@@
 \end{equation*}
-Setting $x=0$ we must have $b_0=b_1^2$. Therefore in order for the recurrence relation to have period 5 we must have $f(z)=cy+c^2$, as desired. 
+Setting $x=0$ we find that $b_0=b_1^2$. Therefore in order for the recurrence relation to have period 5 we must have $f(z)=cy+c^2$, as desired. 
 \end{proof}
 
-We can also perform this analysis for period $6$  
+\subsection{Period 6}
+
+The last case we consider is period 6. Our approach for handling this case is similar to the one we use for period 5. We give the following result.
+
 \begin{proposition}
-If $F$ is of the form in equation ~\ref{eq:firstcase} and has period 6 and $f$ is a polynomial then $f(y) = cy$. 
+If $F(x,y) = f(y)/x$ and $f(y)$ is a polynomial in $y$, then the resulting sequence has period 6 if and only if $f(y) = cy$ for any constant $c$.
 \end{proposition}
+
 \begin{proof}
-It is simple to see that $f(y)=cy$ produces a recurrence of period 6.
-Now we would like to show that all polynomial $f$ must be of this form.
-If we consider some arbitrary $f$ we know that we must have
+It is not hard to see that $f(y) = cy$ produced a recurrence with period 6. The sequence is simply
+\[ x, y, \frac{cy}{x}, \frac{c^2}{x}, \frac{c^2}{y}, \frac{cx}{y}, x,y,\dots .\]
+
+Now we show that all polynomials $f(y)$ that produce period 6 must be of this form. Labeling the terms of the sequence as $a_0, a_1, a_2, \dots$, we get that 
 \begin{align*}
@@
 \end{align*}
-and so $a_5 = \frac{f(x)}{y}$. This also gives us that 
+due to the periodicity condition. From this, we can deduce that $a_5 = \frac{f(x)}{y}$. This also gives us that 
 \begin{equation*}
@@
 \end{equation*}
-Noting that 
+Noting that the recurrence relation gives
 \begin{equation*}
@@
 we obtain 
-\begin{equation}
-\label{period6}
+\begin{equation*}
  f\left( \frac{f(x)}{y} \right) = \frac{ x^2 f(f(f(y)/x)/y)}{f(y)}.
-\end{equation}
+\end{equation*}
 Since $x$ and $y$ can take any values, we can set $y=1$ and let $x$ be arbitrary.
-Furthermore since $f$ is some polynomial it takes the form $f(z) = b_n z^n + \cdots + b_1 z +b_0$.
-Plugging these two into Equation \ref{period6} gives us
+Furthermore since $f$ is some polynomial, it takes the form $f(z) = b_n z^n + \cdots + b_1 z +b_0$.
+Plugging these two into the above equation gives us
 \begin{equation*}
@@
 \end{equation*}
-We note that the largest exponent of $x$ on the left hand side is $n^n$ while the largest exponent of $y$ on the right hand side is $x^2$ if $b_0 \neq 0$.
-Since we can make $x$ arbitrarily large so that the term with the largest exponent dominates, this gives us that we must have $n^n=2$ if $b \neq 0$.
-This equation has no integer solutions and so we must have $b_0 =0$.
-Now if $b_1 \neq 0$ the largest exponent on the right hand side is $1$ and $n^n=1$ is solved by $n=1$ and so $f(z) = b_1 z$ as desired.
+We note that the largest exponent of $x$ in the polynomial on the left hand side is $n^2$ while the largest exponent of $y$ in the polynomial on the right hand side is $x^2$ if $b_0 \neq 0$.
+Since we can make $x$ arbitrarily large so that the term with the largest exponent dominates, this gives $n^2 = 2$ if $b \neq 0$.
+This equation has no integer solutions, so we must have $b_0 =0$.
+Now if $b_1 = 0$ (and $b_0 = 0$), then the highest exponent of $x$ on the right hand side is 0, and so $n^2 = 0$, implying that the entire polynomial is the zero polynomial.
+The function is not periodic in this case.
+This means the only case remaining is when  $b_1 \neq 0$ (and $b_0 = 0$).
+In this case, the same argument as before tells us that $n^2 = 1$, so $n = 1$.
+So the only possible polynomial is $f(z) = b_1 z$ as desired.
 \end{proof}

### 2014-12-08 draft.tex
finished rational and linear f

@@
 \usepackage{amsthm}
+
+\leftmargin=0.25in
+\oddsidemargin=0.25in
+\textwidth=6.0in
+\topmargin=-.4in
+\textheight=9.75in
 
@@
 \label{f(y)/x case}
-\emph{Written by Erik Waingarten and Perry Kleinhenz, edited by Fermi Ma}
+\emph{Written by Erik Waingarten, Perry Kleinhenz, and Fermi Ma}
 
@@
 
+To conclude this section, we observe that this case analysis grew more and more complicated as we increased the desired period.
+This is simply due to the fact that at each step of the recurrence, the expressions grow more and more complicated.
+Thus, this sort of analysis does not seem to be a viable way of coming up with general statements about functions that work for arbitrary periods.
+
 \section{Rational/Linear F}
@@
 \emph{Written by Perry Kleinhenz, edited by Fermi Ma and Erik Waingarten}
-In this section we consider an $F$ which is a rational function composed of arbitrary linear functions. That is 
+
+In this section we consider the case where $F(x,y)$ is the quotient of two linear functions. That is,
 \begin{equation}
 \label{rationallinear}
-F(x,y) = \frac{ b_1 x + b_2 y + b_3}{ c_1 x+ c_2 y + c_3}
+F(x,y) = \frac{ b_1 x + b_2 y + b_3}{ c_1 x+ c_2 y + c_3}.
 \end{equation}
-Recall that our recurrence is $a_{n+1} = F( a_{n-1}, a_n)$. We can write out the first few terms of the sequence with arbitrary starting values $x,y$
-\begin{align}
+
+We approach this problem by considering specific values for the periods.
+In the case of period 2, the only function that works is $F(x,y) = x$, which we get immediately from setting the third term of the sequence equal to the first term.
+For the remainder of this section, we focus on the case where the period is 3.
+
+We first write out the terms of the sequence as given by the recurrence relation:
+\begin{align*}
 a_0 &= x \\ 
-a_1 &=y \\
+a_1 &= y \\
 a_2 &= \frac{ b_1 x + b_2 y + b_3}{ c_1 x+ c_2 y + c_3}\\
-\label{athree}a_3 &= \frac{(c_1 x+ c_2 y + c_3) b_1 y + b_2 (b_1 x + b_2 y + b_3)+ b_3(c_1 x+ c_2 y + c_3)}{ (c_1 x+ c_2 y + c_3)c_1 y+ c_2 (b_1 x + b_2 y + b_3) + c_3(c_1 x+ c_2 y + c_3)} \\
+a_3 &= \frac{(c_1 x+ c_2 y + c_3) b_1 y + b_2 (b_1 x + b_2 y + b_3)+ b_3(c_1 x+ c_2 y + c_3)}{ (c_1 x+ c_2 y + c_3)c_1 y+ c_2 (b_1 x + b_2 y + b_3) + c_3(c_1 x+ c_2 y + c_3)}.\\
 \vdots
-\end{align}
-These expressions get complicated very quickly, but we can use them to classify the periodic behavior of these functions.
+\end{align*}
 
-It is somewhat obvious that $F(x,y)=x$ is the only ratio of linear functions that has period 2, however for larger $n$ the question and answer are slightly more interesting. 
+We now state our main result.
+
 \begin{proposition} 
-If $F(x,y)$ is of the form in Equation \ref{rationallinear} and the recurrence relation it produces has period $3$ then $F$ is one of three following functions:
+If $F(x,y)$ is of the form in Equation \ref{rationallinear} and the recurrence relation it produces has period $3$, then $F(x,y)$ is one of three following functions:
 \begin{align*}
@@
 \begin{proof}
-In order for $F(x,y)$ to induce a recurrence relation with period $3$ we must have $a_3=a_0$. So using the expression in Equation \ref{athree} we must have 
+In order for $F(x,y)$ to induce a recurrence relation with period $3$ we must have $a_3=a_0$. This means that we have
 \begin{align*}
-\left( (c_1 x + c_2 y +c_3) c_1 y + c_2 (b_1 x + b_2 y + b_3) + c_3(c_1 x + c_2 y +c_3) \right) x = \\(c_1 x + c_2 y + c_3) b_1 y + b_2(b_1 x + b_2 y + b_3) + b_3 (c_1 x = c_2 y + c_3),
+\left( (c_1 x + c_2 y +c_3) c_1 y + c_2 (b_1 x + b_2 y + b_3) + c_3(c_1 x + c_2 y +c_3) \right) x = \\(c_1 x + c_2 y + c_3) b_1 y + b_2(b_1 x + b_2 y + b_3) + b_3 (c_1 x = c_2 y + c_3).
 \end{align*}
-If we multiply this expression out we get 
+Expanding out this expression gives
 \begin{align*}
@@
 \end{align*}
-Because this relation must hold for arbitrary $x$ and $y$ we know that terms with the same exponents for $x$ and $y$ must cancel. So for instance we must have 
-\begin{equation*}
-c_1^2 x^2 y = 0, 
-\end{equation*}
+Because this relation must hold for arbitrary $x$ and $y$, the polynomials on both sides must be the same polynomial.
+If they are not, then we have two distinct polynomials that agree at all values of $x$ and $y$, and then their difference is a nonzero polynomial that equals zero everywhere, which is impossible.
+
+So by matching coefficients of terms on the left hand side with coefficients of terms on the right hand side, we get a number of relations.
+For instance, there is a $c_1^2 x^2 y$ term on the left hand side but no $x^2y$ term on the right hand side, so $c_1 = 0$.
+
 and so we must have $c_1=0$. We can do this for terms of each order and find the following 5 relations for the coefficients 
-\begin{align}
+\begin{align*}
 \label{fiverelations}
@@
 b_3(b_2 + c_3) = 0. 
-\end{align}
-Suppose that $c_2 =0$, then $F$ is of the form 
+\end{align*}
+Suppose for now that $c_2 =0$. Then $F$ is of the form 
 \begin{equation*}
@@
 \end{equation*}
-which gives us a new family of relations 
+which gives us a new family of relations.
 \begin{align*}
@@
 \end{align*}
-Combining these two gives us 
+Combining these two equations gives us 
 \begin{equation*}
@@
 \end{equation*}
-which has three solutions $c_3 = -b_2$ and $c_3 = \frac{1}{2} ( b_2 \pm i\sqrt{3}b_2)$.
+which has the solutions $c_3 = -b_2$ and $c_3 = \frac{1}{2} ( b_2 \pm i\sqrt{3}b_2)$.
 Note that $c_3 = -b_2$ implies that we must have $b_1=b_2$ which gives us $F(x,y) = -x -y$.
@@
 \end{align*}
-It is also easy to check that these two $F$ have period 3. This exhausts the possibilities when $c_2=0$ so let us asssume otherwise. Then based on the relations \ref{fiverelations} we must have 
-\begin{equation*}
-b_1 = 0,
-\end{equation*}
-and so $F(x,y)$ takes the form 
+We can also verify that these two functions give a sequence with period 3.
+This exhausts the possibilities when $c_2=0$, so now asssume otherwise.
+Earlier, we had derived the relation $c_2b_1 = 0$.
+If $c_2 = 0$, then $b_1 = 0$, so $F(x,y)$ takes the form
 \begin{equation*}
@@
 \end{equation*}
-Therefore if $a_3 = a_0$ we must have that 
+Therefore if $a_3 = a_0$, we must have that 
 \begin{equation*}
-x = \frac{ b_2^2 y + b_2b_3 +b_3(c_2 y + c_3)}{c_2 b_2 y + c_2 b_3 + c_3 c_2 y + c_3^2},
+x = \frac{ b_2^2 y + b_2b_3 +b_3(c_2 y + c_3)}{c_2 b_2 y + c_2 b_3 + c_3 c_2 y + c_3^2}.
 \end{equation*}
-but the left hand side depends only on $x$ and the right hand side depends only on $y$.
-This relation cannot hold for arbitrary $x,y$ and so we cannot have such $F$.
-Therefore we must have $c_2=0$ and so the only $F$ with period 3 are the ones we have given.
+However, equation cannot hold for arbitrary $x$ and $y$, as the left hand side depends only on $x$ and the right hand side depends only on $y$.
+So $c_2=0$ and so the only functions that produce a sequence with period 3 are the ones we have given.
 \end{proof}
+
+Given how complex the expression for $a_3$ was, we did not consider the case of period 4, as that would require analyzing $a_4$.
+This motivates the need for a different approach to considering the case of arbitrary periods, which we present in the following section.
 

### 2014-12-08 draft.tex
Edits to Section 4

@@
 
-Consider the case where $F(x,y) = f(y)/x$ where $f(y) = y^n$. Then the sequence can be written as follows
-\[ x^1y^0, x^0y^1, x^{-1}y^{n}, x^{-n}y^{n^2-1}, x^{-n^2+1}y^{n^3-2n},x^{-n^3+n^2+n}y^{n^4-3n^2+1}, \dots \]
+In this section we consider the case where $F(x,y) = f(y)/x$ where $f(y) = y^n$, where $n$ can be any complex number, not just an integer.
+The question we would like to answer is given an integer $p$ can we always come up with an $n$ such that $F$ has period $p$.
+We first explore some basic properties of the sequences such functions produce and compute an explicit example.
+We then give an explicit formula for the $k$th term in the sequence.
+Finally using a generating function we are able to produce a necessary condition for $n$, to produce a sequence with period $p$.
+Using Mathematica we verified numerically for values of $p$ up to 1000 that this necessary condition is also sufficient and because of this we conjecture
+\begin{conjecture}
+\label{cos}
+Given any integer $p>2$ let 
+\begin{equation*}
+n = 2 \cos(2 \pi l/p),
+\end{equation*}
+with $l \in \{1,2,3, \ldots, p-1 \}$. Then $F(x,y) = y^n/x$ is periodic with period $p$.
+\end{conjecture}
 
-The interesting thing to note is that all of the terms in the sequence are now monomials.
-This makes the analysis much easier.
+We begin by considering the sequence produced by $F(x,y) = y^n/x$ 
+\begin{equation*}
+x^1y^0, x^0y^1, x^{-1}y^{n}, x^{-n}y^{n^2-1}, x^{-n^2+1}y^{n^3-2n},x^{-n^3+n^2+n}y^{n^4-3n^2+1}, \dots \,.
+\end{equation*}
+
+The interesting thing to note is that all of the terms in the sequence are now monomials, which will simplify our analysis.
 Now let $\alpha_k$ be the sequence of the exponents of $x$ in the above sequence, and let $\beta_k$ be the sequence of exponents of $y$.
-So we have
+We can easily compute the first few terms of the sequence
 \begin{align*}
@@
 \alpha_6 &= -n^4+3n^2 -1 &\beta_6& =n^5-4n^3+3n \\ 
-\alpha_7 &= -n^5+4n^3 - 3n &\beta_7& =n^6-5n^4+6n^2 - 1
+\alpha_7 &= -n^5+4n^3 - 3n &\beta_7& =n^6-5n^4+6n^2 - 1.
 \end{align*}
@@
 
-In our numerical calculations, it seems like this system of equations always \emph{does} has a real solution, which leads us to conjecture that for any period strictly greater than 2, there is a function of the form $y^n/x$ with that period.
-
-\subsection{Properties of $\alpha_k$ and $\beta_k$}
-
+We now give an explicit form for $\alpha_k$ and $\beta_k$ in terms of $k$ and $n$. Unfortunately we are not able to show that the equations these produce always have common solutions. 
 We first notice that $\alpha_k$ and $\beta_k$ are similar sequences, as they can be defined as
@@
 
-We also have a relation between $\alpha_k$ and $\beta_k$. 
+We note further that there is a relation between different terms of the two sequences.  
 \begin{lemma} 
@@
 
-We also note that $\beta_k$ can be written as 
+\begin{proposition} 
+For $k \geq 1$
 \begin{align*}
-\binom{k-1}{k-1} n^{k-1} - \binom{k-2}{k-3}n^{k-3} +\binom{k-3}{k-5}n^{k-5} -\binom{k-4}{k-7}n^{k-7} + \dots \\
+\beta_k = \binom{k-1}{k-1} n^{k-1} - \binom{k-2}{k-3}n^{k-3} +\binom{k-3}{k-5}n^{k-5} -\binom{k-4}{k-7}n^{k-7} + \dots \\
 =\sum_{i = 0}^{\lfloor (k-1)/2 \rfloor} (-1)^i\binom{k-1-i}{k-1-2i}n^{k-1-2i}\\
 \end{align*}
-for $k \geq 1$.
-
-To check this, note that it holds for $k = 1$ and $k = 2$, and then plug it in to the recurrence relation
+\end{proposition}
+\begin{proof}
+It is easy to check that this holds for $k = 1$ and $k = 2$.  If we plug it in to the recurrence relation
+\begin{equation*}
+\beta_k = n\beta_{k-1} - \beta_{k-2},
+\end{equation*}
+we must have 
 \begin{align*}
-\beta_k =& n\beta_{k-1} - \beta_{k-2}\\
 \sum_{i = 0}^{\lfloor (k-1)/2 \rfloor} (-1)^i\binom{k-1-i}{k-1-2i}n^{k-1-2i} = & n \sum_{i = 0}^{\lfloor (k-2)/2 \rfloor} (-1)^i\binom{k-2-i}{k-2-2i}n^{k-2-2i} \\
@@
 \end{align*}
-Checking this equation for when $k$ is even and when $k$ is odd, as well as using combinatorial identities, shows that this is true.
+Checking this equation when $k$ is even and when $k$ is odd, as well as using combinatorial identities, shows that this expression for $\beta_k$ satisfies the recurrence relation.
+Because of this the expression must equal $\beta_k$ for $k \geq 1$.
+\end{proof}
 
-So we have an expression for $\beta_k$, and this in turn gives us an expression for $\alpha_k$ as noted above.
-Thus, we know that if we want to attain a specific period $p$, we have to solve equations involving these known expressions.
+So we have an expression for $\beta_k$, which in turn gives us an expression for $\alpha_k$ by Lemma \ref{ab}.
+Thus, we know that if we want to attain a specific period $p$, we have to solve four equations involving these known expressions.
 
-It remains to show that these equations always produce a real solution for $n$.
-
-\subsection{Existence of Common Solutions}
-
-Now if we want to choose an $n$ such that  $F(x,y)$ has period $p$, our choice of $n$ must solve the equations 
-\begin{align*}
-x^{\alpha_p} y^{\beta_p} = x^{1}y^{0} \\
-x^{\alpha_{p+1}} y^{\beta_{p+1}} = x^{0}y^{1}.
-\end{align*}
-Or in other terms
+In fact thes four equations are 
 \begin{align*}
@@
 \end{align*}
-However as shown in Lemma \ref{ab} above $\alpha_{p+1} = -\beta_p$, and so $\beta_p=0$ and $\alpha_{p+1} =0$ are the same equation.  We also know by the recurrence relation for $\beta$ that 
+As shown in Lemma \ref{ab} above $\alpha_{p+1} = -\beta_p$,  $\beta_p=0$ and $\alpha_{p+1} =0$ are the same equation so we actually only need to find a value for $n$ which satisfies the three equations
+\begin{align*}
+\alpha_p &=1 \\
+\beta_p &=0\\ 
+\beta_{p+1} &= 1.
+\end{align*}
+It remains to show that these equations always produce a real solution for $n$.
+\\
+
+Now using a generating function approach we give a necessary condition for $n$. 
+First we must produce the generating function for $\alpha_k$.
+Recall that a generating function of an infinite sequence is a formal power series with coefficients equal to the terms of the sequence.
+So if $G(\xi)$ is the generating function of $\alpha_k$, then
 \begin{equation*}
-\beta_{p+1} = n \beta_{p} - \beta_{p-1}.
+G(\xi) = \sum_{k=0}^{\infty} \alpha_k \xi^k,
 \end{equation*}
-Substituting $\alpha_p = -\beta_{p-1}$ and $\beta_{p}=0$ gives us 
+where $\xi$ is some formal variable. We can find a closed form expression for $G(\xi)$.
+
+\begin{lemma} For a given $n$ the generating function for $\alpha_k$ is 
 \begin{equation*}
-\beta_{p+1} = \alpha_p.
+G(\xi) = \frac{ 1 - n\xi}{1 - n \xi + \xi^2} .
 \end{equation*}
-Therefore we actually only need to find a value for $n$ which satisfies the two equations
-\begin{align*}
-\alpha_p &=1\\
-\alpha_{p+1}&=0.
-\end{align*}
-
-\subsection{Generating Function for $\alpha_k$}
-If we have the recurrence relation for $\alpha_k$ 
+\end{lemma}
+\begin{proof}
+Recall the recurrence relation for $\alpha_k$ 
 \begin{equation*}
@@
 \end{equation*}
-we can use generating functions to find a closed form for $\alpha$. If we let $G(\xi)$ be the generating function of $\alpha_k$, that is 
-\begin{equation*}
-G(\xi) = \sum_{k=0}^{\infty} a_k \xi^k,
-\end{equation*}
-then using the above recurrence relation we know that 
-\begin{equation*}
-G(\xi) -\alpha_0 - \alpha_1 \xi = n \xi G(\xi) - n \alpha_0 \xi - \xi^2 G(\xi).
-\end{equation*}
-W e can see that this holds as 
+and note that 
 \begin{align*}
@@
 \end{align*}
-Therefore we can see 
+So if we subtract the second and third equations from the first and simplify using the recurrence relation we see 
 \begin{equation*}
-G( \xi) (1-n \xi + \xi^2) = n\alpha_0 + \alpha_1 \xi - n\alpha_0 \xi,
+G(\xi) - n \xi G(\xi) - \xi^2 G(\xi) = \alpha_0 + \alpha_1 \xi - n \alpha \xi.
 \end{equation*}
-and so simplifying and using the fact that $\alpha_0=1, \alpha_1=0$ gives us 
+Rearranging this equation we can see 
 \begin{equation*}
-G(\xi) = \frac{ 1 - n\xi}{1 - n \xi + \xi^2} .
+G( \xi) (1-n \xi + \xi^2) = n\alpha_0 + \alpha_1 \xi - n\alpha_0 \xi.
 \end{equation*}
-Now we recall that our goal is to establish what $n$ we must choose in order for our sequence to be periodic of period $p$.
-In order for this to occur we must have $\alpha_p= \alpha_0$ and $\alpha_{p+1} = \alpha_1$.
-This gives us that
-\begin{align*}
-G(\xi) = &\alpha_0 + \alpha_1 \xi + \alpha_2 \xi^2 + \cdots + \alpha_{p-1} \xi^{p-1} \\
-+ \alpha_p(&\alpha_0 + \alpha_1 \xi + \alpha_2 \xi^2 + \cdots + \alpha_{p-1} \xi^{p-1}) \\ 
-+ \cdots 
-\end{align*}
-and so 
+Using the fact that $\alpha_0=1, \alpha_1=0$ and rearranging gives us
+\begin{equation*}
+G(\xi) = \frac{ 1 - n\xi}{1 - n \xi + \xi^2},
+\end{equation*}
+as desired.
+\end{proof}
+
+We can also find another expression for $G(\xi)$ if we assume that the sequence is periodic. 
+\begin{lemma} If $n$ is such that $F$ produces a sequence of period $p$ then the generating function for $\alpha_k$ is 
 \begin{equation*}
@@
 \end{equation*}
-Combining these two relations gives us that if our sequence is of period $p$ then 
+\end{lemma}
+\begin{proof}
+In order for the period of $F$ to be $p$ we must have $\alpha_p= \alpha_0$ and $\alpha_{p+1} = \alpha_1$. Plugging that into the power series form of $G(\xi)$ tells us that
+\begin{align*}
+G(\xi) = &\alpha_0 + \alpha_1 \xi + \alpha_2 \xi^2 + \cdots + \alpha_{p-1} \xi^{p-1} \\
++ \xi^p(&\alpha_0 + \alpha_1 \xi + \alpha_2 \xi^2 + \cdots + \alpha_{p-1} \xi^{p-1}) \\ 
++ \cdots \, ,
+\end{align*}
+and so using the summation formula for geometric series we have
+\begin{equation*}
+G(\xi) = \frac{1}{1- \xi^p} (\alpha_0 + \alpha_1 \xi + \alpha_2 \xi^2 + \cdots + \alpha_{p-1} \xi^{p-1}).
+\end{equation*}
+\end{proof}
+
+Using these two expressions for the generating function we can produce the following necessary condition for $n$. 
+\begin{proposition} 
+\label{must}
+If $n$ is such that $F$ produces a sequence of period $p$ then $n$ must be of the form
+\begin{equation*}
+n= 2 \cos(2 \pi l/p), 
+\end{equation*}
+for some $l \in \{0,1,2, \ldots, p-1\}$. 
+\end{proposition}
+\begin{proof}
+If we equate the two different expressions for $G(\xi)$ we have 
 \begin{equation*}
@@
 \end{equation*}
-We can deduce additional properties of $n$ from this relation. Note that in order to have equality of rational functions, the zeroes of the functions on both sides must be the same. 
-The only zero on the left hand side is $\xi = 1/n$, (note that $1-n*1/n + 1/n^2 \neq 0$).
+
+Note that in order to have equality of rational functions, the zeroes of the functions on both sides must be the same. 
+The only zero on the left hand side is $\xi = 1/n$, (note that it is not a zero of the denominator).
 The numerator of the left hand side has $p-1$ zeroes in the complex plane, while the denominator has exactly $p$ zeroes.
@@
 \end{align*}
-So $n$ must be the sum of some $p$th roots of unity, and in fact these roots of unity must be conjugates of one another, so $n$ is always real and 
+So $n$ must be the sum of some $p$th roots of unity, and in fact these roots of unity must be conjugates of one another, so $n$ is always real. Therefore  
 \begin{equation*}
@@
 for some $l \in \{0, 1,2, \ldots, p-1\}$. 
-Since the $\alpha_k$ are the coefficients of the power series of $G(\xi)$ we also know that 
+\end{proof}
+Note that by Proposition \ref{period6} we know that $F(x,y)=y/x$ has period 6, and since a function $F$ can only have one period for $p \neq 6$, $l$ cannot equal 0.
+
+We conclude this section with some conjectures based on numerical evidence.
+
+\begin{conjecture} For all $p$ there exists $n$ such that $F(x,y)=y^n/x$ has period $p$. 
+\end{conjecture} 
+This conjecture is equivalent to saying that we can always find a value of $n$ that satisfies the three equations 
+\begin{align*}
+\alpha_p &=1\\ 
+\beta_p &=0\\
+\beta_{p+1} &=1.
+\end{align*}
+We have verified that solutions exist for values of $p$ up to 1000.
+Note that this conjecture along with Proposition \ref{must} are not equivalent to Conjecture \ref{cos}, which for ease of reading we restate here.
+\begin{conjecture}
+Given any integer $p>2$ let 
 \begin{equation*}
-\alpha_k = \frac{1}{k!} \frac{d^k}{d \xi^k} G(\xi) |_{\xi=0}.
+n = 2 \cos(2 \pi l/p),
 \end{equation*}
+with $l \in \{1,2,3, \ldots, p-1 \}$. Then $F(x,y) = y^n/x$ is periodic with period $p$.
+\end{conjecture}
+Conjecture \ref{cos} states that for \emph{any} value of $l$ the $n$ produced has the desired period, while Conjecture
 

### 2014-12-08 draft.tex
Section 4 done

@@
 
-In this section we consider the case where $F(x,y) = f(y)/x$ where $f(y) = y^n$, where $n$ can be any complex number, not just an integer.
+In this section we consider the case where $F(x,y) = f(y)/x$ with $f(y) = y^n$, where $n$ is any complex number, not just an integer.
 The question we would like to answer is given an integer $p$ can we always come up with an $n$ such that $F$ has period $p$.
@@
 We then give an explicit formula for the $k$th term in the sequence.
-Finally using a generating function we are able to produce a necessary condition for $n$, to produce a sequence with period $p$.
-Using Mathematica we verified numerically for values of $p$ up to 1000 that this necessary condition is also sufficient and because of this we conjecture
+Finally using a generating function we are able to produce a necessary condition on $n$, in order for $F$ to produce a sequence with period $p$.
+Using Mathematica we were able to verify numerically for values of $p$ up to 1000 that this necessary condition is also sufficient.
+Because of this we conjecture
 \begin{conjecture}
@@
 We begin by considering the sequence produced by $F(x,y) = y^n/x$ 
-\begin{equation*}
+\begin{equation}
+\label{exponents}
 x^1y^0, x^0y^1, x^{-1}y^{n}, x^{-n}y^{n^2-1}, x^{-n^2+1}y^{n^3-2n},x^{-n^3+n^2+n}y^{n^4-3n^2+1}, \dots \,.
-\end{equation*}
+\end{equation}
 
-The interesting thing to note is that all of the terms in the sequence are now monomials, which will simplify our analysis.
-Now let $\alpha_k$ be the sequence of the exponents of $x$ in the above sequence, and let $\beta_k$ be the sequence of exponents of $y$.
+We note that all of the terms in the sequence are now monomials, which simplifies our analysis. For simplicity we introduce the following notation.
+\begin{definition} 
+Let $\alpha_k$ be the sequence of exponents of $x$ in Equation \ref{exponents}, and $\beta_k$ be the sequence of exponents of $y$ in Equation \ref{exponents}.
+\end{definition}
 We can easily compute the first few terms of the sequence
@@
 \end{align*}
+We can use these sequences $\{\alpha_i\}$ and $\{\beta_i\}$ to compute values for $n$ that achieve certain periods. In particular if we can find an $n$ which solves the four equations 
+\begin{align*}
+\alpha_p &= 1 \\
+\beta_p &=0\\
+\alpha_{p+1} &=  0\\
+\beta_{p+1}&=1,
+\end{align*}
+then $F(x,y)=y^n/x$ has period $p$.
 
-We can use these $\{\alpha_i\}$ and $\{\beta_i\}$ sequences to get values of $n$ that achieve certain periods.
 For example, if we want a function of the form $F(x,y) = y^n/x$ with period 5, we simply set $\alpha_5 = \alpha_0 = 1$, $\beta_5 = \beta_0 = 0$, $\alpha_6 = \alpha_1 = 0$, and $\beta_6 = \beta_1 = 1$.
@@
 \end{align*}
-There is no guarantee that this system has a solution, but it turns out that setting $n = -\frac{1+\sqrt{5}}{2} = \phi$, the golden ratio, works.
-This tells us that $F(x,y) = y^{-\phi}/x$ is periodic with period 5, and we can indeed check that this is the case.
+There is no guarantee that this system has a solution, but in fact $n = -\frac{1+\sqrt{5}}{2} = -\phi$, the golden ratio, is a solution.
+This tells us that $F(x,y) = y^{-\phi}/x$ is periodic with period 5, and we can check that indeed this is the case.
 
-We now give an explicit form for $\alpha_k$ and $\beta_k$ in terms of $k$ and $n$. Unfortunately we are not able to show that the equations these produce always have common solutions. 
+We now give explicit formulas for $\alpha_k$ and $\beta_k$ in terms of $k$ and $n$. Unfortunately we are not able to show that the equations these produce always have common solutions. 
 We first notice that $\alpha_k$ and $\beta_k$ are similar sequences, as they can be defined as
@@
 As a base case note that $\alpha_1 = 0 = \beta_0$, and $\alpha_2 = -n = \beta_1$.
-Now if we assume this holds for $k \leq m$ and would like to show it holds for $k = m+1$ consider $\alpha_{m+1}$
+Now if we assume this holds for $k \leq m$ and would like to show it holds for $k = m+1$ consider $\alpha_{m+1}$ which by the recurrence relation is
 \begin{equation*}
@@
 \end{equation*}
-Well $\alpha_m = -\beta_{m-1}$ and $\alpha_{m-1} = - \beta_{m-2}$ and so 
+Well $\alpha_m = -\beta_{m-1}$ and $\alpha_{m-1} = - \beta_{m-2}$ by the induction hypothesis and so 
 \begin{equation*}
-\alpha_{m+1} = - n \beta_{m-1} + \beta_{m-2} = -\beta_{m},
+\alpha_{m+1} = - n \beta_{m-1} + \beta_{m-2} = -\beta_{m}.
 \end{equation*}
-as desired.
 \end{proof}
+Note that this Lemma also reduces the number of simultaneous equations that we need to solve from four to three as we always have $\alpha_{p+1} = - \beta_{p}$.
+Both are set to zero so it is enough to only include one of them in the system of equations
 
+We now given an exact formula for $\beta_k$ 
 \begin{proposition} 
 For $k \geq 1$
+%= \binom{k-1}{k-1} n^{k-1} - \binom{k-2}{k-3}n^{k-3} +\binom{k-3}{k-5}n^{k-5} -\binom{k-4}{k-7}n^{k-7} + \dots \\
 \begin{align*}
-\beta_k = \binom{k-1}{k-1} n^{k-1} - \binom{k-2}{k-3}n^{k-3} +\binom{k-3}{k-5}n^{k-5} -\binom{k-4}{k-7}n^{k-7} + \dots \\
-=\sum_{i = 0}^{\lfloor (k-1)/2 \rfloor} (-1)^i\binom{k-1-i}{k-1-2i}n^{k-1-2i}\\
+\beta_k =\sum_{i = 0}^{\lfloor (k-1)/2 \rfloor} (-1)^i\binom{k-1-i}{k-1-2i}n^{k-1-2i}
 \end{align*}
@@
 \begin{proof}
-It is easy to check that this holds for $k = 1$ and $k = 2$.  If we plug it in to the recurrence relation
+It is easy to check that this holds for $k = 1$ and $k = 2$.  If we plug the formula into the recurrence relation
 \begin{equation*}
@@
 \end{align*}
-Checking this equation when $k$ is even and when $k$ is odd, as well as using combinatorial identities, shows that this expression for $\beta_k$ satisfies the recurrence relation.
-Because of this the expression must equal $\beta_k$ for $k \geq 1$.
+Checking this equation separately when $k$ is even or odd, as well as using combinatorial identities, shows that this expression for $\beta_k$ satisfies the recurrence relation.
+Because of this our formula is valid for $k \geq 1$.
 \end{proof}
 
-So we have an expression for $\beta_k$, which in turn gives us an expression for $\alpha_k$ by Lemma \ref{ab}.
-Thus, we know that if we want to attain a specific period $p$, we have to solve four equations involving these known expressions.
-
-In fact thes four equations are 
+This expression for $\beta_k$, gives us an expression for $\alpha_k$ by Lemma \ref{ab}. In order to obtain a function $F$ with period $p$ we must solve the three equations
 \begin{align*}
@@
 \beta_p &=0\\ 
-\alpha_{p+1} &= 0 \\
-\beta_{p+1} &= 1.
+\beta_{p+1} &= 1,
 \end{align*}
-As shown in Lemma \ref{ab} above $\alpha_{p+1} = -\beta_p$,  $\beta_p=0$ and $\alpha_{p+1} =0$ are the same equation so we actually only need to find a value for $n$ which satisfies the three equations
-\begin{align*}
-\alpha_p &=1 \\
-\beta_p &=0\\ 
-\beta_{p+1} &= 1.
-\end{align*}
-It remains to show that these equations always produce a real solution for $n$.
+plugging in the explicit values for $\alpha_p, \beta_p$ and $\beta_{p+1}$. We were not able to show that these equations always produce a solution for $n$.
 \\
 
-Now using a generating function approach we give a necessary condition for $n$. 
-First we must produce the generating function for $\alpha_k$.
-Recall that a generating function of an infinite sequence is a formal power series with coefficients equal to the terms of the sequence.
+Now using a generating function approach, given a desired period $p$, we give a necessary condition for $n$. 
+First we produce the generating function for $\alpha_k$.
+A generating function of an infinite sequence is a formal power series with coefficients equal to the terms of the sequence.
 So if $G(\xi)$ is the generating function of $\alpha_k$, then
@@
 
-\begin{lemma} For a given $n$ the generating function for $\alpha_k$ is 
+\begin{lemma} The generating function for $\alpha_k$ is 
 \begin{equation*}
@@
 \begin{align*}
-G(\xi) &= \alpha_0 + &\alpha_1 \xi + &\alpha_2 \xi^2 + \cdots \\
-n \xi G(\xi) &= &n\alpha_0 \xi + &n\alpha_1 \xi^2 + n\alpha_2 \xi^3 + \cdots \\
-\xi^2 G(\xi) &= &&\alpha_0 \xi^2 + \alpha_1 \xi^3 + \alpha_2 \xi^4 + \cdots.
+G(\xi) &= \alpha_0 + \> \alpha_1 \xi + \>\> \alpha_2 \xi^2 + \cdots \\
+n \xi G(\xi) &= \qquad n\alpha_0 \xi + n\alpha_1 \xi^2 + n\alpha_2 \xi^3 + \cdots \\
+\xi^2 G(\xi) &= \qquad \qquad \quad \quad \alpha_0 \xi^2 + \alpha_1 \xi^3 +  \cdots.
 \end{align*}
-So if we subtract the second and third equations from the first and simplify using the recurrence relation we see 
+So if we subtract the second and third equations from the first, simplify using the recurrence relation and rearrange terms we obtain
 \begin{equation*}
-G(\xi) - n \xi G(\xi) - \xi^2 G(\xi) = \alpha_0 + \alpha_1 \xi - n \alpha \xi.
+G( \xi) (1-n \xi + \xi^2) = \alpha_0 + \alpha_1 \xi - n\alpha_0 \xi.
 \end{equation*}
-Rearranging this equation we can see 
-\begin{equation*}
-G( \xi) (1-n \xi + \xi^2) = n\alpha_0 + \alpha_1 \xi - n\alpha_0 \xi.
-\end{equation*}
-Using the fact that $\alpha_0=1, \alpha_1=0$ and rearranging gives us
-\begin{equation*}
-G(\xi) = \frac{ 1 - n\xi}{1 - n \xi + \xi^2},
-\end{equation*}
-as desired.
+Using the fact that $\alpha_0=1, \alpha_1=0$ and rearranging gives the desired result.
 \end{proof}
@@
 \begin{align*}
-G(\xi) = &\alpha_0 + \alpha_1 \xi + \alpha_2 \xi^2 + \cdots + \alpha_{p-1} \xi^{p-1} \\
-+ \xi^p(&\alpha_0 + \alpha_1 \xi + \alpha_2 \xi^2 + \cdots + \alpha_{p-1} \xi^{p-1}) \\ 
-+ \cdots \, ,
+G(\xi) =&  \qquad \> \alpha_0 + \alpha_1 \xi + \alpha_2 \xi^2 + \cdots + \alpha_{p-1} \xi^{p-1} \\
+ &+ \xi^p(\alpha_0 + \alpha_1 \xi + \alpha_2 \xi^2 + \cdots + \alpha_{p-1} \xi^{p-1}) \\ 
+ &+ \xi^{2p}(\alpha_0 + \alpha_1 \xi + \alpha_2 \xi^2 + \cdots + \alpha_{p-1} \xi^{p-1}) \\ 
+ &+ \cdots \, ,
 \end{align*}
-and so using the summation formula for geometric series we have
-\begin{equation*}
-G(\xi) = \frac{1}{1- \xi^p} (\alpha_0 + \alpha_1 \xi + \alpha_2 \xi^2 + \cdots + \alpha_{p-1} \xi^{p-1}).
-\end{equation*}
+and using the summation formula for geometric series gives us our desired result.
 \end{proof}
@@
 \label{must}
-If $n$ is such that $F$ produces a sequence of period $p$ then $n$ must be of the form
+If $F$ produces a sequence of period $p$ then $n$ must be of the form
 \begin{equation*}
@@
 \end{equation*}
-for some $l \in \{0,1,2, \ldots, p-1\}$. 
+for some $l \in \{1,2, \ldots, p-1\}$. 
 \end{proposition}
 \begin{proof}
-If we equate the two different expressions for $G(\xi)$ we have 
+Both expressions for $G(\xi)$ are valid and so we can equate them 
 \begin{equation*}
@@
 Note also that the locations of discontinuities for both functions must be the same.
-Therefore we must have that the zeroes of $1-n\xi + \xi^2$ are the same as those zeroes of the denominator of the left hand side which were not canceled out.
-Thus for some $l$ and $m$, we must have
+Therefore the zeroes of $1-n\xi + \xi^2$ must be the same as those zeroes of the denominator of the right hand side which were not canceled out.
+Thus for some $s$ and $t$, we must have
 \begin{align*}
-(\xi - e^{2 \pi i l/p})(\xi - e^{2 \pi i m/p}) = 1 - n \xi + \xi^2,
+(\xi - e^{2 \pi i s/p})(\xi - e^{2 \pi i t/p}) = 1 - n \xi + \xi^2,
 \end{align*}
-or 
+or written another way
 \begin{align*}
-n = e^{2 \pi i l/p} + e^{2 \pi i m/p} \\
-1 = e^{2 \pi i (l+m)/p}.
+n = e^{2 \pi i s/p} + e^{2 \pi i t/p} \\
+1 = e^{2 \pi i (s+t)/p}.
 \end{align*}
-So $n$ must be the sum of some $p$th roots of unity, and in fact these roots of unity must be conjugates of one another, so $n$ is always real. Therefore  
+So $n$ must be the sum of two distinct $p$th roots of unity, and in fact these roots of unity must be conjugates of one another, so $n$ is always real. Therefore  
 \begin{equation*}
@@
 \end{equation*}
-for some $l \in \{0, 1,2, \ldots, p-1\}$. 
+for some $l \in \{1,2, \ldots, p-1\}$. 
 \end{proof}
-Note that by Proposition \ref{period6} we know that $F(x,y)=y/x$ has period 6, and since a function $F$ can only have one period for $p \neq 6$, $l$ cannot equal 0.
 
@@
 
-\begin{conjecture} For all $p$ there exists $n$ such that $F(x,y)=y^n/x$ has period $p$. 
+\begin{conjecture}
+\label{exists}
+ For all $p$ there exists $n$ such that $F(x,y)=y^n/x$ has period $p$. 
 \end{conjecture} 
@@
 \end{align*}
-We have verified that solutions exist for values of $p$ up to 1000.
+We have been able to verify that solutions exist for values of $p$ up to 1000.
 Note that this conjecture along with Proposition \ref{must} are not equivalent to Conjecture \ref{cos}, which for ease of reading we restate here.
@@
 \end{conjecture}
-Conjecture \ref{cos} states that for \emph{any} value of $l$ the $n$ produced has the desired period, while Conjecture
+Conjecture \ref{cos} states that for \emph{any} value of $l$ the $n$ produced has the desired period, while Conjecture \ref{exists} along with Proposition \ref{must} states that one such $l$ exists such that the $n$ produced has the desired period.
+It is more computationally intensive to check if certain values of $n$ produce periodic functions and so we were able to verify this conjecture only for $p$ up to 100.
+
+\section{Haikus} 
+Its periodic  \\
+What came before is what's next \\
+Its periodic \\ \\
+No matter the $p$ \\
+You can find a few good $n$\\
+That is what we hope \\
 

### 2014-12-10 draft.tex
project done

@@
 \newtheorem{lemma}{Lemma}
+\newtheorem{conjecture}{Conjecture}
 
@@
 Because of this we conjecture
+
 \begin{conjecture}
@@
 \begin{proof}
-We will show this using induction.
-As a base case note that $\alpha_1 = 0 = \beta_0$, and $\alpha_2 = -n = \beta_1$.
-Now if we assume this holds for $k \leq m$ and would like to show it holds for $k = m+1$ consider $\alpha_{m+1}$ which by the recurrence relation is
+We will show this using induction. As a base case note that $\alpha_1 = 0 = \beta_0$, and $\alpha_2 = -n = \beta_1$. Now we assume this holds for $k \leq m$. To show it holds for $k = m+1$, consider
 \begin{equation*}
@@
 \end{equation*}
-Well $\alpha_m = -\beta_{m-1}$ and $\alpha_{m-1} = - \beta_{m-2}$ by the induction hypothesis and so 
+We have $\alpha_m = -\beta_{m-1}$ and $\alpha_{m-1} = - \beta_{m-2}$ by the induction hypothesis and so 
 \begin{equation*}
@@
 \sum_{i = 0}^{\lfloor (k-1)/2 \rfloor} (-1)^i\binom{k-1-i}{k-1-2i}n^{k-1-2i} = & n \sum_{i = 0}^{\lfloor (k-2)/2 \rfloor} (-1)^i\binom{k-2-i}{k-2-2i}n^{k-2-2i} \\
-& +\sum_{i = 0}^{\lfloor (k-3)/2 \rfloor} (-1)^i\binom{k-3-i}{k-3-2i}n^{k-3-2i}\\
+& +\sum_{i = 0}^{\lfloor (k-3)/2 \rfloor} (-1)^i\binom{k-3-i}{k-3-2i}n^{k-3-2i}.\\
 \end{align*}
-Checking this equation separately when $k$ is even or odd, as well as using combinatorial identities, shows that this expression for $\beta_k$ satisfies the recurrence relation.
-Because of this our formula is valid for $k \geq 1$.
+We omit the steps of explicitly checking the equation, but simple combinatorial identities show that both sides are equal. Thus, our formula is valid for $k \geq 1$.
 \end{proof}
 
-This expression for $\beta_k$, gives us an expression for $\alpha_k$ by Lemma \ref{ab}. In order to obtain a function $F$ with period $p$ we must solve the three equations
+This expression for $\beta_k$ gives us an expression for $\alpha_k$ by Lemma \ref{ab}. In order to obtain a function $F$ with period $p$ we must solve the three equations
 \begin{align*}
@@
 \end{align*}
-plugging in the explicit values for $\alpha_p, \beta_p$ and $\beta_{p+1}$. We were not able to show that these equations always produce a solution for $n$.
+for $n$. We were not able to show that these equations always produce a solution, despite the fact that we know the explicit form of these equations for any $p$.
 \\
 
-Now using a generating function approach, given a desired period $p$, we give a necessary condition for $n$. 
+Now we switch our focus and use a generating function approach to this problem. We show a necessary condition for $n$ so that $y^n/x$ produces a sequence with a given $p$.
+
 First we produce the generating function for $\alpha_k$.
-A generating function of an infinite sequence is a formal power series with coefficients equal to the terms of the sequence.
-So if $G(\xi)$ is the generating function of $\alpha_k$, then
+Note that we shift from looking at $\beta_k$ to looking at $\alpha_k$ simply to make the generating function formulation simpler.
+However, we know from Lemma~\ref{ab} that these two sequences are almost interchangeable.
+
+A generating function of an infinite sequence is a formal power series with coefficients equal to the terms of the sequence.  So if $G(\xi)$ is the generating function of $\alpha_k$, then 
 \begin{equation*}
@@
 \section{Haikus} 
+\emph{Perry's Haikus}\\
+
+\noindent Its periodic  \\
+What came before is what's next \\
 Its periodic \\
-What came before is what's next \\
-Its periodic \\ \\
-No matter the $p$ \\
+
+\noindent No matter the $p$ \\
 You can find a few good $n$\\
@@
 
+\noindent\emph{Fermi's Haikus}\\
+
+\noindent Try small cases first.\\
+Two, three, and four seem simple.\\
+Five and six less so.\\
+
+\noindent Restrict attention\\
+To the $y$ to the $n$ case.\\
+Now it always works!\\
+
+\noindent We can prove this claim.\\
+Just write the equations down.\\
+Shoot, how does this work?\\
+
 \end{document}
